### 2024-10-22 paper/paper.qmd
update paper rough draft

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "Using Aggregated Polling Data to Predict the Outcome of the 2024 Presidential Race"
author: 
  - Andy Jiang
  - Onon Burentuvshin
  - Rui Hu
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
date: today
date-format: long
abstract: "The 2024 U.S. presidential election is shaping up to be a highly competitive race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome. This paper aims to build a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election. The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions. Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process. The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts. Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readr)
library(here)
library(knitr)
library(kableExtra)

data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
```

# Introduction
The 2024 U.S. presidential election is shaping up to be one of the most closely watched and potentially pivotal elections in recent history. As public opinion shifts and political dynamics evolve, polling data has emerged as a critical tool for forecasting the outcome and understanding voter preferences. Polls provide a snapshot of where candidates stand at various points in time, reflecting the impact of campaigns, debates, and major events. However, the reliability and accuracy of individual polls can vary significantly based on methodology, sample size, and other factors, making it necessary to aggregate multiple sources of data for a more robust prediction.

This paper aims to forecast the outcome of the 2024 U.S. presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race. By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion. Additionally, the paper examines the methodologies of different pollsters to assess their strengths and weaknesses, which can help identify possible biases in the aggregated data.

The analysis will further explore the geographic distribution of support across key battleground states, providing insights into the electoral landscape. Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts. By integrating multiple data sources and critically evaluating polling practices, this study aims to contribute to the ongoing discussion on the role of polling in democratic processes and election forecasting.

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

```{r}
#| echo: false
#| warning: false
#| message: false

# Set seed for reproducibility
set.seed(316)

sample_data <- data %>% sample_n(10)

# Display the sampled data as a table with smaller text
kable(sample_data, caption = "Sample of 10 Random Observations from the Analysis Data") %>%
  kable_styling(font_size = 8)  # Adjust the font size as needed
```

```{r}

```

## Predictor variables

# Model

## Model set-up

### Model justification

# Results

```{r}
#| echo: false
#| warning: false
#| message: false
data_filtered <- data %>% filter(candidate_name %in% c("Donald Trump", "Kamala Harris"))

# Now proceed with calculating the average polling percentage by state
data_avg <- data_filtered %>%
  group_by(state, candidate_name) %>%
  summarize(avg_pct = mean(pct, na.rm = TRUE))

# Plotting the average polling percentages by state
ggplot(data_avg, aes(x = reorder(state, avg_pct), y = avg_pct, fill = candidate_name)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Average Polling Percentages by State",
       subtitle = "Comparing Support for Trump and Harris Across States",
       x = "State",
       y = "Average Polling Percentage",
       fill = "Candidate") +
  coord_flip() +  # Flip coordinates for easier reading
  theme_minimal()
```

```{r}

```

# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

```{r}

```

## Diagnostics

```{r}

```

\newpage

# References

### 2024-10-22 scripts/02-download_data.R

@@ -15,6 +15,4 @@ the_raw_data <- read.csv("data/01-raw_data/president_polls.csv")
 
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "data/01-raw_data/raw_data.csv") 
-
-         
+write_csv(the_raw_data, "data/01-raw_data/raw_data.csv")

### 2024-10-22 scripts/00-simulate_data.R
Simulate data.

@@ -1,49 +1,53 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of US electoral divisions, including the 
+#state and party that won each division.
+# Author: Rui Hu, 
+# Date: 22 October 2024
+# Contact: hr.hu@mail.utoronto.ca, 
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+set.seed(304)
 
 
 #### Simulate data ####
 # State names
 states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+  "Pennsylvania",
+  "Arizona",
+  "Montana",
+  "Florida",
+  "Texas",
+  "Nebraska CD-2",
+  "Michigan",
+  "Ohio",
+  "Wisconsin",
+  "Georgia",
+  "North Carolina",
+  "Nevada",
+  "Virginia"
 )
 
 # Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+parties <- c("DEM", "REP", "GRE", "IND", "LIB", "CON", "PSL")
 
 # Create a dataset by randomly assigning states and parties to divisions
 analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
+  division = paste("Division", 1:200),  # Add "Division" to make it a character
   state = sample(
     states,
-    size = 151,
+    size = 200,
     replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
+    prob = c(0.085, 0.047, 0.007, 0.142, 0.193, 0.005, 0.067, 0.078, 0.039, 
+             0.07, 0.069, 0.021, 0.057) # Rough state population distribution
   ),
   party = sample(
     parties,
-    size = 151,
+    size = 200,
     replace = TRUE,
[…]

### 2024-10-22 scripts/00-simulate_data.py

@@ -1,57 +1,0 @@
-#### Preamble ####
-# Purpose: Simulates a dataset of US electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
-
-#### Workspace setup ####
-library(tidyverse)
-set.seed(304)
-
-
-#### Simulate data ####
-# State names
-states <- c(
-  "Pennsylvania",
-  "Arizona",
-  "Montana",
-  "Florida",
-  "Texas",
-  "Nebraska",
-  "Michigan",
-  "Ohio",
-  "Wisconsin",
-  "Georgia",
-  "North Carolina",
-  "Nevada",
-  "Virginia"
-)
-
-# Political parties
-parties <- c("DEM", "REP", "GRE", "LIB", "IND")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
-)
-
-
-#### Save data ####
-write_csv(analysis_data, "data/00-simulated_data/simulated_data.csv")

### 2024-10-22 paper/paper.qmd
Update paper.qmd
Added justification for why New York Times was selected for our pollster.

@@
 # Appendix {-}
+Sampling Methodology Employed by New York Times and Siena College:
+
+	Our analysis and prediction utilizes data collected by a single pollster and it is important to scrutinize the sampling methodology behind the sampling methods used to determine the extent of the external validity of our predictions.
+Primarily, the data gathered by New York Times was done so with the collaboration with Siena College through live-interviewers reaching voters by telephone.
+	The poll targets registered voters in the United States, with a particular focus on voters in battleground states for presidential races.
+Although this focus is emphasized and accounted for, their target population is the population of registered voters in the United States of America.
+The sampling frame is the voter file, a comprehensive database of registered voters that includes demographic information, voting history, and contact details.
+And from this sampling frame, respondents are randomly selected, balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
+	The poll relies on random digit dialing to reach voters, predominantly via cellphones (over 90% of calls).
+While landlines are also called, the dominance of cellphone usage aligns with contemporary communication trends.
+This results in their rendition of random sampling, which contributes to the external validity of proper usage of data.
+However, though the sample was selected randomly, reaching voters by phone has become more difficult due to low response rates (around 2%), requiring many attempts to secure responses from certain individuals.
+Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states.
+This also raises the concern of selection bias as younger voters that display a propensity for digital communication might be underrepresentted.
+	The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting.
+Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data.
+Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
+Experiments with alternative methods, such as mail surveys, have shown some differences, particularly in political engagement levels, but not in overall vote preferences.
+
+Sampling Approach: Stratified Sampling
+
+Method: Stratified sampling is used, where different voter groups are targeted based on their demographic and regional characteristics.
+For battleground state polls, the sample is drawn from states likely to decide the election, such as Arizona, Georgia, and Pennsylvania.
+
+Trade-offs: While phone polling allows for broad geographic reach and is quick to execute, it faces declining response rates and potential underrepresentation of certain groups.
+The reliance on phone surveys limits the ability to reach voters without reliable phone access, and it may inadvertently bias results towards those who are more reachable by phone.
+
+Questionnaire
+
+The Times/Siena Poll carefully crafts its questions to be fair and balanced, ensuring that respondents from across the political spectrum feel their views are represented.
+The team devotes significant time to wording questions to avoid leading respondents or introducing bias.
+The questionnaire is kept relatively short (under 15 minutes), helping to reduce respondent fatigue and minimize dropout rates during the interview.
+Phone polls may not capture the full nuance of voter opinions due to the limited nature of phone conversations compared to online or face-to-face methods.
+Furthermore, telephone-based interviews with voters presents the danger of selection bias discussed earlier.
+As a result, while the poll's margin of error for the overall population is typically 3 to 4 percentage points, smaller subgroups may have larger margins of error due to smaller sample sizes.
 

### 2024-11-01 paper/paper.qmd
Update paper.qmd
Updated appendix and idealized methodology

@@
 Primarily, the data gathered by New York Times was done so with the collaboration with Siena College through live-interviewers reaching voters by telephone.
-	The poll targets registered voters in the United States, with a particular focus on voters in battleground states for presidential races.
-Although this focus is emphasized and accounted for, their target population is the population of registered voters in the United States of America.
-The sampling frame is the voter file, a comprehensive database of registered voters that includes demographic information, voting history, and contact details.
+	The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
+Consequently, the target population is registered voters of the United States of America and the sampling frame is the national list of registered voters from which NYC employs random sampling to create their pollsters.
 And from this sampling frame, respondents are randomly selected, balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
-	The poll relies on random digit dialing to reach voters, predominantly via cellphones (over 90% of calls).
+	The poll relies on random digit dialing to reach voters, predominantly via cell phones.
 While landlines are also called, the dominance of cellphone usage aligns with contemporary communication trends.
-This results in their rendition of random sampling, which contributes to the external validity of proper usage of data.
-However, though the sample was selected randomly, reaching voters by phone has become more difficult due to low response rates (around 2%), requiring many attempts to secure responses from certain individuals.
-Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states.
-This also raises the concern of selection bias as younger voters that display a propensity for digital communication might be underrepresentted.
+This results in their rendition of random sampling, which contributes to the external validity of data.
+However, though the sample was selected randomly, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
+Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling.
+Although this can be seen as random sampling, the concern of low response rates and reliance on dialing to reach voters raises concerns of selection bias.
+There are questions as to whether a certain demographic will be more responsive to being reached through a cell phone.
+Moreover, voters that are reached over the phone may feel the urge to provide more ‘socially desirable’ responses that are not reflective of their true opinions.
+	With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics.
 The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting.
@@
 Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
-Experiments with alternative methods, such as mail surveys, have shown some differences, particularly in political engagement levels, but not in overall vote preferences.
+Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% (New York Times).
 
@@
 Method: Stratified sampling is used, where different voter groups are targeted based on their demographic and regional characteristics.
-For battleground state polls, the sample is drawn from states likely to decide the election, such as Arizona, Georgia, and Pennsylvania.
+For battleground state polls, the sample is drawn from states likely to decide the election, such as Arizona, North Carolina, Georgia, and Pennsylvania.
 
@@
 Furthermore, telephone-based interviews with voters presents the danger of selection bias discussed earlier.
-As a result, while the poll's margin of error for the overall population is typically 3 to 4 percentage points, smaller subgroups may have larger margins of error due to smaller sample sizes.
+
+2	Idealized Methodology
+
+	Pursuant to accurately predicting the winner of the presidential election with the electoral college system, there are assumptions that need to be assessed.
+The United States of America’s electoral college system creates a special environment where votes in some states are disproportionately more influential than that of others and candidates are not elected based on popular vote, but on the majority of electoral votes they get.
+
+Assumption 1:  Nation-level Popular Vote is irrelevant in our methodology since president electors are chosen based on electoral votes.
+
+Assumption 2:  Based on historical and polling data, some states’ electoral votes are predetermined as either Democrat or Republican.
+Therefore, it is more prudent to shift focus over to swing states where outcomes are uncertain.
+This assumption is accompanied with the challenge of determining what states qualify as “swing states”.
+However, on this issue, there is consensus on which states qualify as battleground states.
+As of 2024, our methodology should direct all our resources to acquiring voting data on the following states (New York Times).
+Pennsylvania
+Georgia
+North Carolina
+Michigan
+Arizona
+Wisconsin
+Nevada
+
+2.1	Feasibility of Reaching Voters: Justification of Online Panels
+
+According to the New York Times, with a sample of 1000 individual votes, there is a margin of error of around three to four percentages.
+With $100,000, there are limitations on the labor and resources that is required to poll 1000 voters while balancing out demographics through dialing.
+Furthermore, there is additional filtering of our sample frame to determine likely voters.
+Assuming New York Times’ 2% voter response rate, to sample 1000 voters, at least 50,000 voters will need to be called.
+It is likely that our team will be dialing way more than 50,000 times since it is an unreasonable assumption that every voter we call would pick up or be available to provide a response.
+There is also the fact that our team does not carry the same credibility and history of acquiring poll data as the New York Times does, resulting in more reluctance for voters to share information with us.
+Therefore, it is not feasible for our methodology to employ telephone dialing as our method to reach voters.
+Instead, we focus on online panels and surveys with incentives for completing the survey correctly.
+However, online panels and surveys come with their own set of challenges and weaknesses that must be addressed in our methodology.
+Primarily, the problem of self-selection in online panels disrupts the random selection that allows the external validity of our predictions.
+There is a strong possibility that we acquire responses from respondents that are not likely to vote, gaining data from outside our target population.
+Even if we distribute the panels randomly among swing states, responses are still corrupted by selection bias that occurs from responses that are provided from demographics that feel more passionately about the election or are more likely to respond to online panels.
+As we do with telephone dialing, we have less control over the specific demographic we want to target, resulting in a less stratified data that is representative of the target population overall.
+
+2.2	Remedies for Online Panels
+
+2.2.1	Weighting Adjustments
+
+Although online panels offer an imperfect solution to the limited resources our team will work with, there are remedies that can address underrepresentation brought by selection bias.
+As NYC and Siena College does, post-survey weighting can help us represent our target population more accurately.
+This is an effective way to adjust our sample based on demographic data and historical turnout patterns within each state.
+By weighting responses to mirror actual voter demographics, the survey results can approximate a more realistic projection of the electorate.
+
+2.2.2	Screening for Likely Voters
+
+	To produce accurate predictions of election results, our sample needs to be acquired from a target population that participates in the election.
+Therefore, it becomes necessary to include screening questions designed to filter for likely voters, based on voting history or engagement levels.
+Our survey includes questions that pertain to voting history, interest and engagement, voting intention, and eligibility.
+Responses to these questions will be used to produce an aggregate “likely voter” score that filters for the target population enabling for more accurate predictions of the presidential election.
+
+2.3	Elements of Our Survey
+To gather accurate responses from a diverse and representative set of likely voters, our survey design carefully adheres to best practices in methodology.
+Given our goal to avoid attrition bias, we’ve restricted the estimated survey completion time to under ten minutes.
+This constraint is stricter than the fifteen-minute benchmark typically used by NYC and Siena College for telephone surveys, as online surveys require shorter durations to maintain respondent engagement.
+Our survey is divided into three main sections: Preamble, Eligibility, and Party Affiliation.
+The survey we constructed can be found in Appendix B.
+2.3.1	Preamble
+The Preamble serves as an introductory section that aims to establish transparency and motivate respondents to complete the survey accurately.
+This introduction begins with an explanation of the lottery-style incentive offered for survey completion.
+Rather than small individual payments, participants have a chance to win a larger prize if they complete the survey, a choice that aligns with budget constraints while enhancing participation rates.
+To encourage honest responses, respondents are assured of the anonymity of their answers, as well as the fact that their responses will be used solely for research purposes.
+This transparency fosters trust and can reduce hesitation when sharing political preferences.
+Information about the survey’s purpose is provided sparingly to minimize any potential response bias, as we communicate that the survey concerns voting and political engagement while omitting specific details that could influence responses, such as particular issues or candidate names.
+Additionally, respondents have the option to input a referral code if invited by a friend or family member, which can increase their chances of winning the lottery and encourage participation through word-of-mouth.
+We also request information on the relationship with the referrer to monitor potential demographic clustering in cases where social or familial ties might influence responses.
+
+2.3.2	Eligibility
+The Eligibility section focuses on ensuring that respondents meet the criteria necessary for inclusion in our target population, specifically targeting likely voters within designated swing states to improve the relevance and accuracy of our sample for election predictions.
+This section begins by asking for respondents' state of residence, age, race, and other preliminary demographic information.
+To further narrow our sample to those most likely to vote, we employ several screening questions related to voting history, political engagement, and voting intentions.
+These questions help exclude individuals who are unlikely to participate in the election, thus refining our sample to reflect the likely voting population.
+
+2.3.3	Party Affiliation
+Party Affiliation addresses respondents’ political leanings and past voting behavior.
+This section explores their current preference for presidential candidates and parties and asks how they voted in previous elections.
+By differentiating between party and candidate preference, we can identify any variance in their voting behavior and assess whether respondents’ decisions align more strongly with party or individual candidate considerations.
+This section also explores whether respondents are informed about their choices, asking questions to determine whether they are aware of both candidates or have researched their policies.
+By gathering these insights, we can create a profile of the respondent’s political orientation, which allows for a nuanced interpretation of voting intentions that goes beyond simple party preference.
+
+2.4 Distribution of Online Panels
+The online panel method provides valuable flexibility in how surveys are distributed, enabling targeted outreach in regions crucial to our election prediction model.
+Since the distribution strategy will absorb a significant portion of the budget, this section outlines our plan for cost-effective, targeted, and controlled distribution, aimed at achieving a sample that represents voters in key swing states while addressing biases inherent to online panel surveys.
+
+2.4.1 Swing State Representation
+To capture a meaningful sample for predicting election results, we target respondents exclusively from key swing states where voting outcomes remain uncertain.
+By focusing our resources on swing states, we enhance the relevance of our sample to the Electoral College system, which relies heavily on swing state outcomes.
+Achieving this requires not only careful selection of digital platforms but also strategic advertising in locally relevant spaces.
+The lottery-style incentive, with a $5,000 voucher offered to one lucky respondent, serves as an appealing motivator designed to increase participation.
+We will advertise the survey on websites, forums, and marketplaces that have high traffic within our target states.
+Examples include social media channels, local news sites, and state-specific online communities.
+Additionally, we may utilize geo-targeted ads on platforms like Google and Facebook to directly reach residents of these swing states, optimizing our budget by focusing on the digital spaces our target demographic frequents.
+A significant portion of the budget will thus be allocated to these state-specific online advertisements, which not only promote the survey but also help ensure that respondents fit our target profile.
+
+2.4.2 Referral Mechanics
+To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey.
+Each referral allows the original respondent to gain an additional entry in the lottery, increasing their chances of winning.
+This referral incentive taps into snowball sampling, where respondents refer people within their network to participate, expanding our pool of respondents organically.
+However, using snowball sampling in an election survey introduces potential biases, particularly the risk of overrepresentation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies.
+To mitigate this, we will place specific restrictions on the referral program.
+Each respondent will be limited to referring only one other individual, minimizing the potential for overly clustered referrals.
+Additionally, we will require respondents to identify their relationship with each referral, helping us monitor homogeneity in our responses.
+By balancing the benefits of snowball sampling with these restrictions, we aim to expand the reach of our survey into difficult to reach demographics without compromising the representativeness of the sample.
 

### 2024-11-01 paper/paper.qmd
update result and discussion

@@
 abstract: "The 2024 U.S.
-presidential election is shaping up to be a highly competitive race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome.
+presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome.
 This paper aims to build a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election.
@@
 
-The analysis will further explore the geographic distribution of support across key battleground states, providing insights into the electoral landscape.
+The analysis will further explore the geographic distribution of support across key swing states, providing insights into the electoral landscape.
 Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts.
@@
 
-sample_data <- data %>% sample_n(10)
+# Sample 10 random observations from the filtered data with Trump and Harris
+sample_data <- data %>%
+  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
+  sample_n(10)
 
-# Display the sampled data as a table with smaller text
+# Display the sampled data as a table with smaller text and adjusted column spacing
 kable(sample_data, caption = "Sample of 10 Random Observations from the Analysis Data") %>%
-  kable_styling(font_size = 8)  # Adjust the font size as needed
+  kable_styling(font_size = 8, full_width = FALSE) %>%  # Set full_width to FALSE to center the table
+  column_spec(1:ncol(sample_data), width = "2cm")  # Adjust width as needed, here set to 2cm per column
+
 ```
@@
 # Results
+The analysis of polling data across key swing states for the 2024 U.S.
+Presidential Election reveals insights into the levels of support for candidates Donald Trump and Kamala Harris.
+The findings are presented through three primary visualizations: the average polling percentage by state, the distribution of polling percentages, and the difference in average polling percentage between the two candidates.
+
+## Average Polling Percentage by State
+From @fig-1, we can see that in the swing states of Arizona, Georgia, and North Carolina, Trump holds a narrow lead.
+In contrast, Harris leads in Pennsylvania, Wisconsin, Nevada, and Michigan.
+When looking at the overall average across these states, Harris slightly edges out Trump, indicating her overall advantage in these swing areas.
+
+## Polling Percentage Distribution
+The box plot in @fig-2 demonstrates the range and consistency of support for both candidates across each state.
+Trump shows a wider range of support, reflecting variability, while Harris has relatively steady polling percentages across states, maintaining higher consistency.
+Harris’s support is less variable and generally centers around higher polling percentages compared to Trump’s.
+
+## Difference in Average Polling Percentage
+@fig-3 highlights the difference in average polling percentages by state, with positive values indicating Trump’s lead and negative values indicating Harris's.
+Trump’s lead in the three states (Arizona, Georgia, and North Carolina) is relatively narrow, with margins of less than 1 percent.
+In contrast, Harris’s lead in the states favoring her (Pennsylvania, Wisconsin, Nevada, and Michigan) ranges from 1 to 4 percent, indicating her stronger support in the states where she leads.
 
 ```{r}
+#| label: fig-1
+#| fig-cap: "Average Polling Percentage by State"
 #| echo: false
@@
 #| message: false
-data_filtered <- data %>% filter(candidate_name %in% c("Donald Trump", "Kamala Harris"))
+# Calculate the average polling percentage by state for Trump and Harris
+data_avg <- data %>%
+  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
+  group_by(state, candidate_name) %>%
+  summarize(avg_pct = mean(pct, na.rm = TRUE), .groups = "drop")
 
-# Now proceed with calculating the average polling percentage by state
-data_avg <- data_filtered %>%
-  group_by(state, candidate_name) %>%
-  summarize(avg_pct = mean(pct, na.rm = TRUE))
+# Calculate the overall average polling percentage for Trump and Harris
+overall_avg <- data %>%
+  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
+  group_by(candidate_name) %>%
+  summarize(avg_pct = mean(pct, na.rm = TRUE)) %>%
+  mutate(state = " Overall")  # Add a space before "Overall" to separate it visually
 
-# Plotting the average polling percentages by state
-ggplot(data_avg, aes(x = reorder(state, avg_pct), y = avg_pct, fill = candidate_name)) +
-  geom_bar(stat = "identity", position = "dodge") +
+# Combine state-level data with overall average
+combined_data <- bind_rows(data_avg, overall_avg)
+
+# Ensure "Overall" appears at the bottom with spacing
+combined_data$state <- factor(combined_data$state, levels = c(setdiff(unique(combined_data$state), " Overall"), " Overall"))
+
+# Plot the average polling percentages by state with overall comparison
+ggplot(combined_data, aes(x = state, y = avg_pct, fill = candidate_name)) +
+  geom_bar(stat = "identity", position = position_dodge(width = 0.8), aes(color = ifelse(state == " Overall", "Overall", "State")), width = 0.6) + 
+  scale_color_manual(values = c("Overall" = "black", "State" = NA), guide = "none") +  # Add dark grey outline for "Overall" bars
+  scale_fill_manual(values = c("Donald Trump" = "#F8766D", "Kamala Harris" = "#56B4E9")) +  # Custom colors for consistency
   labs(title = "Average Polling Percentages by State",
-       subtitle = "Comparing Support for Trump and Harris Across States",
        x = "State",
@@
   coord_flip() +  # Flip coordinates for easier reading
-  theme_minimal()
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    axis.text.y = element_text(margin = margin(r = 10)), # Add spacing to y-axis labels
+    panel.grid.major.y = element_blank(), # Remove y-axis gridlines for clarity
+    panel.spacing = unit(1, "lines") # Increase panel spacing
+  )
+
 ```
@@
 ```{r}
+#| label: fig-2
+#| fig-cap: "Polling Percentage Distribution"
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(data %>% filter(candidate_name %in% c("Donald Trump", "Kamala Harris")), 
+       aes(x = state, y = pct, fill = candidate_name)) +
+  geom_boxplot(alpha = 0.7) +
+  labs(title = "Polling Percentage Distribution by State",
+       x = "State",
+       y = "Polling Percentage",
+       fill = "Candidate") +
+  scale_fill_manual(values = c("Donald Trump" = "#F8766D", "Kamala Harris" = "#56B4E9")) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+```
+```{r}
+#| label: fig-3
+#| fig-cap: "Difference in Average Polling Percentage"
+#| echo: false
+#| warning: false
+#| message: false
+data_diff <- data %>%
+  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
+  group_by(state) %>%
+  summarize(diff_pct = mean(pct[candidate_name == "Donald Trump"], na.rm = TRUE) - 
+                      mean(pct[candidate_name == "Kamala Harris"], na.rm = TRUE), .groups = "drop")
 
+ggplot(data_diff, aes(x = reorder(state, diff_pct), y = diff_pct, fill = diff_pct > 0)) +
+  geom_bar(stat = "identity", color = "darkgrey") +
+  scale_fill_manual(values = c("TRUE" = "#F8766D", "FALSE" = "#56B4E9"), 
+                    labels = c("Kamala Harris", "Donald Trump")) +
+  labs(title = "Difference in Average Polling Percentage by State",
+       x = "State",
+       y = "Difference in Polling Percentage",
+       fill = "Lead") +
+  coord_flip() +
+  theme_minimal() +
+  theme(legend.position = "bottom")
 ```
@@
 
-## First discussion point {#sec-first-point}
+## Impact of Key Demographics and Policy Appeals
+Harris’s lead in several swing states may be influenced by her campaign’s appeal to key demographic groups, particularly immigrants.
+The Democratic platform has emphasized social and economic benefits for immigrant communities, which may have strengthened her base in states with significant immigrant populations.
+Policies that promise support for healthcare, education, and other public services are likely contributing to Harris’s appeal among these groups, solidifying her lead in states like Nevada and Michigan.
+This demographic support provides Harris with a strategic advantage, as these communities may play a crucial role in voter turnout and loyalty.
 
-## Second discussion point
+## Influence of Endorsements and High-Profile Backing
+Recently, high-profile figures like Elon Musk have publicly backed Trump, using their influence to mobilize support for his campaign.
+Musk’s endorsement may energize Trump’s voter base, especially among his followers and individuals interested in business and technology.
+This kind of visible support from influential figures could affect last-minute voter decisions, particularly in tightly contested states where Trump’s lead is slim.
+If Musk’s endorsement translates into increased campaign funding or social media influence, it could bolster Trump’s standing in swing states where the margin remains close, potentially altering the final outcome on November 5th.
 
-## Third discussion point
+## Limitations of the Analysis: Focus on Swing States
+While the analysis focuses on key swing states, it does not consider the broader national picture, which includes states with clear, one-sided advantages for either candidate.
+This narrowed focus on swing states provides insights into swing areas but does not give a complete picture of the national landscape.
+Therefore, while Harris appears to have an edge in these swing states, it is unclear whether she is leading overall.
+The situation in solidly red or blue states could still shift the electoral balance, meaning Trump could potentially gain ground through strong performances in traditionally Republican states.
 
-## Weaknesses and next steps
+## Potential Influence of Late Campaign Efforts
+With a few days remaining before the election, both campaigns are likely to intensify their outreach efforts, particularly in swing states.
+Trump’s recent increase in targeted advertisements and campaign rallies in swing states could energize his supporters, narrowing Harris’s lead.
+On the other hand, Harris’s campaign may focus on mobilizing key demographics, such as young and minority voters, to secure her advantage.
+Late-breaking events, public debates, or controversies could sway undecided voters and ultimately impact the election results in these states.
+
+## Limitations and Next Steps
+This analysis is limited to examining current polling data in swing states and does not account for unexpected shifts in voter sentiment or turnout on election day.
+Additionally, focusing exclusively on swing states omits the influence of non-swing states that may still play a role in the electoral vote tally.
+Future analyses could incorporate national polling data to provide a more comprehensive perspective and examine demographic breakdowns within each state to understand which groups are driving support for each candidate.
+Integrating data on recent campaign activities, endorsements, and voter sentiment on pressing issues could also improve the predictive accuracy of election outcomes.
 
@@
 Method: Stratified sampling is used, where different voter groups are targeted based on their demographic and regional characteristics.
-For battleground state polls, the sample is drawn from states likely to decide the election, such as Arizona, North Carolina, Georgia, and Pennsylvania.
+For swing state polls, the sample is drawn from states likely to decide the election, such as Arizona, North Carolina, Georgia, and Pennsylvania.
 
@@
 This assumption is accompanied with the challenge of determining what states qualify as “swing states”.
-However, on this issue, there is consensus on which states qualify as battleground states.
+However, on this issue, there is consensus on which states qualify as swing states.
 As of 2024, our methodology should direct all our resources to acquiring voting data on the following states (New York Times).

### 2024-11-01 scripts/03-clean_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rui Hu, 
+# Purpose: Cleans the raw data into 7 swing states
+# Author: Rui Hu, Andy Jiang
 # Date: 21 October 2024
-# Contact: hr.hu@mail.utoronto.ca, 
+# Contact: hr.hu@mail.utoronto.ca, ayx.jiang@mail.utoronto.ca
 # License: N/A
 # Pre-requisites: N/A
 
@@ -14,9 +14,11 @@ library(tidyverse)
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 
 cleaned_data <- raw_data |> 
-  filter(population == "rv", numeric_grade >=3) |>
-  select(pollster,state,start_date,end_date,question_id,sample_size,
-           population,party,answer,candidate_name,hypothetical, pct)
+  filter(population == "rv", 
+         state %in% c("Pennsylvania", "Georgia", "North Carolina", 
+                      "Michigan", "Arizona", "Wisconsin", "Nevada")) |>
+  select(pollster, state, start_date, end_date, question_id, sample_size,
+         population, party, answer, candidate_name, hypothetical, pct)
 
 #### Save data ####
 write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")

### 2024-11-03 scripts/03-clean_data.R
Update clean data.

@@ -22,3 +22,23 @@ cleaned_data <- raw_data |>
 
 #### Save data ####
 write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")
+
+#### Clean data for model####
+# Read the data
+data <- read.csv("data/02-analysis_data/analysis_data.csv")
+
+# Change the form of date
+data$end_date <- mdy(data$end_date)
+data_filtered <- data %>%
+  mutate(end_date_numeric = as.numeric(end_date))
+
+# Selct the true polls
+data_filtered <- data_filtered %>%
+  filter(hypothetical == FALSE, !is.na(sample_size))
+
+data_filtered <- data_filtered %>% 
+  group_by(end_date_numeric, candidate_name, end_date)%>% 
+  summarise(average_pct = mean(pct, na.rm = TRUE))
+
+#### Save data ####
+write_csv(data_filtered, "data/02-analysis_data/model_data.csv")

### 2024-11-03 scripts/06-model_data.R
Update model data.

@@ -13,25 +13,18 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+data_filtered <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
+data_filtered <- data_filtered %>% mutate(pct = average_pct / 100)
+
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+model <- glm(pct ~ end_date_numeric + candidate_name, data = data_filtered, 
+             family = binomial(link = "logit"))
+summary(model)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  model,
+  file = "models/model.rds"
 )
-
-

### 2024-11-03 paper/paper.qmd
Update paper.

@@
 # Model details {#sec-model-details}
+```{r}
+data_filtered <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
+data_filtered <- data_filtered %>%
+  mutate(predicted_pct = predict(penn_model, newdata = ., type = "response"))
+summary(penn_model)
+
+ggplot(penn, aes(x = start_date_numeric, y = pct, color = candidate_name)) +
+  geom_point(aes(y = pct), alpha = 0.5) + 
+  geom_line(aes(y = predicted_pct), size = 1) + 
+  labs(title = "Pennsylvania - Predicted vs True",
+       x = "Date",
+       y = "Rate of support") +
+  theme_minimal() +
+  scale_y_continuous(labels = scales::percent_format())
+
+```
 

### 2024-11-04 paper/paper.qmd
Add files via upload
Updated  appendix and removed sections we are  not using. References still need to be added  and  is in progress.

--- 2024-11-01 paper/paper.qmd
@@
 
-# Appendix {-}
-Sampling Methodology Employed by New York Times and Siena College:
+# Appendix A {-}
+
+#  Sampling Methodology Employed by New York Times and Siena College:
 
@@
 Consequently, the target population is registered voters of the United States of America and the sampling frame is the national list of registered voters from which NYC employs random sampling to create their pollsters.
-And from this sampling frame, respondents are randomly selected, balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
+And from this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
 The poll relies on random digit dialing to reach voters, predominantly via cell phones.
@@
 
-Sampling Approach: Stratified Sampling
+# Sampling Approach: Stratified Sampling
 
-Method: Stratified sampling is used, where different voter groups are targeted based on their demographic and regional characteristics.
-For swing state polls, the sample is drawn from states likely to decide the election, such as Arizona, North Carolina, Georgia, and Pennsylvania.
+##  Methodology
+The Times/Siena Poll employs a stratified random sampling approach to ensure that the sample accurately represents the diversity within the target population of registered voters in the United States.
+This method involves dividing the population into distinct subgroups, or “strata,” based on key characteristics such as state, age, gender, race, education level, and political affiliation.
+For example, in presidential elections, particular emphasis is placed on voters from swing states like Arizona, North Carolina, Georgia, and Pennsylvania.
+By focusing on these battleground states, the poll aims to capture the opinions of voters who are most likely to influence the election outcome.
+Once the strata are established, respondents are randomly selected within each group, ensuring that all demographic groups are appropriately represented in proportion to their actual distribution within the electorate.
 
-Trade-offs: While phone polling allows for broad geographic reach and is quick to execute, it faces declining response rates and potential underrepresentation of certain groups.
-The reliance on phone surveys limits the ability to reach voters without reliable phone access, and it may inadvertently bias results towards those who are more reachable by phone.
+## Advantages
+Stratified sampling offers the advantage of higher precision in representing the population's diversity, as each subgroup is proportionally represented.
+By breaking down the sample into distinct groups, the Times/Siena Poll can adjust for demographic variations between states or voter groups, which is particularly useful in a diverse electorate.
+This approach helps to minimize sampling error by ensuring that all significant voter subgroups are included, thus increasing the reliability of the poll’s predictions.
 
-Questionnaire
+## Challenges and Trade-offs
 
-The Times/Siena Poll carefully crafts its questions to be fair and balanced, ensuring that respondents from across the political spectrum feel their views are represented.
-The team devotes significant time to wording questions to avoid leading respondents or introducing bias.
-The questionnaire is kept relatively short (under 15 minutes), helping to reduce respondent fatigue and minimize dropout rates during the interview.
-Phone polls may not capture the full nuance of voter opinions due to the limited nature of phone conversations compared to online or face-to-face methods.
-Furthermore, telephone-based interviews with voters presents the danger of selection bias discussed earlier.
+Although stratified sampling improves representativeness, it presents certain challenges in execution.
+First, identifying and reaching a sufficient number of respondents from harder-to-reach groups (such as young voters, minority populations, and those without reliable phone access) can be difficult, especially given the 2% response rate.
+To counterbalance the low response rates, the poll requires multiple call attempts and careful post-survey weighting to adjust for any potential underrepresentation.
+Additionally, while phone polling offers broad geographic reach and a standardized mode of data collection, it limits the sample to voters with phone access who are willing to participate in phone interviews, potentially introducing selection bias if certain demographics are less reachable by phone.
 
-2	Idealized Methodology
+# Idealized Methodology
 
@@
 
-Assumption 1:  Nation-level Popular Vote is irrelevant in our methodology since president electors are chosen based on electoral votes.
+## Assumption 1:
 
-Assumption 2:  Based on historical and polling data, some states’ electoral votes are predetermined as either Democrat or Republican.
+Nation-level Popular Vote is irrelevant in our methodology since president electors are chosen based on electoral votes.
+
+##  Assumption 2:
+
+Based on historical and polling data, some states’ electoral votes are predetermined as either Democrat or Republican.
 Therefore, it is more prudent to shift focus over to swing states where outcomes are uncertain.
@@
 However, on this issue, there is consensus on which states qualify as swing states.
+Pollsters such as  New York Times have their metric for determining which  states are 'battleground states'.
 As of 2024, our methodology should direct all our resources to acquiring voting data on the following states (New York Times).
+This assumption results in each presidential candidate starting off with a set number of electoral votes.
+
+##  Swing States
+
+According to 2024 polling data conducted by New York Times, the swing states are determined to be the following:
+
 Pennsylvania
@@
 
-2.1	Feasibility of Reaching Voters: Justification of Online Panels
+## Feasibility of Reaching Voters: Justification of Online Panels
 
@@
 Primarily, the problem of self-selection in online panels disrupts the random selection that allows the external validity of our predictions.
-There is a strong possibility that we acquire responses from respondents that are not likely to vote, gaining data from outside our target population.
+Moreover, there is apossibility that we acquire responses from respondents that are not likely to vote, gaining data from outside our target population.
 Even if we distribute the panels randomly among swing states, responses are still corrupted by selection bias that occurs from responses that are provided from demographics that feel more passionately about the election or are more likely to respond to online panels.
-As we do with telephone dialing, we have less control over the specific demographic we want to target, resulting in a less stratified data that is representative of the target population overall.
+Unlike telephone dialing, we have less control over the specific demographic we want to target, resulting in a less stratified data that is representative of the target population overall.
 
-2.2	Remedies for Online Panels
+##	Remedies for Online Panels
 
-2.2.1	Weighting Adjustments
+### Weighting Adjustments
 
@@
 This is an effective way to adjust our sample based on demographic data and historical turnout patterns within each state.
-By weighting responses to mirror actual voter demographics, the survey results can approximate a more realistic projection of the electorate.
+By weighting responses to mirror actual voter demographics from a particular state, the survey results can approximate a more realistic projection of the electorate.
+These weighting adjustments help to maintain the integrity of our sample, closely resembling the target population of a state.
 
-2.2.2	Screening for Likely Voters
+### Screening for Likely Voters
 
-	To produce accurate predictions of election results, our sample needs to be acquired from a target population that participates in the election.
+Although weighting adjustments helps  us represent our  target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels.
+To produce accurate predictions of election results, our sample needs to be acquired from a target population that will participate in the election.
 Therefore, it becomes necessary to include screening questions designed to filter for likely voters, based on voting history or engagement levels.
@@
 
-2.3	Elements of Our Survey
+##  Elements of Our Survey
 To gather accurate responses from a diverse and representative set of likely voters, our survey design carefully adheres to best practices in methodology.
@@
 The survey we constructed can be found in Appendix B.
-2.3.1	Preamble
+
+### Preamble
 The Preamble serves as an introductory section that aims to establish transparency and motivate respondents to complete the survey accurately.
@@
 
-2.3.2	Eligibility
+### Eligibility
 The Eligibility section focuses on ensuring that respondents meet the criteria necessary for inclusion in our target population, specifically targeting likely voters within designated swing states to improve the relevance and accuracy of our sample for election predictions.
@@
 
-2.3.3	Party Affiliation
+###  Party Affiliation
 Party Affiliation addresses respondents’ political leanings and past voting behavior.
@@
 
-2.4 Distribution of Online Panels
+##  Distribution of Online Panels
 The online panel method provides valuable flexibility in how surveys are distributed, enabling targeted outreach in regions crucial to our election prediction model.
@@
 
-2.4.1 Swing State Representation
+###   Swing State Representation
 To capture a meaningful sample for predicting election results, we target respondents exclusively from key swing states where voting outcomes remain uncertain.
@@
 
-2.4.2 Referral Mechanics
+###   Referral Mechanics
 To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey.
@@
 
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-```{r}
-
-```
-
-## Diagnostics
-
-```{r}
-
-```
-
 \newpage
 
+# Appendix B
+
+##  Idealized Questionnaire and Survey
+
+https://docs.google.com/forms/d/117wC8f1rBW_bd5glEdiR-7823-02A3HiD5EzQuT1GVw/edit
+
 # References

### 2024-11-04 scripts/03-clean_data.R
Clean data.

@@ -9,6 +9,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
+install.packages("arrow")
+library(arrow)
 
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_data.csv")
@@ -21,11 +23,11 @@ cleaned_data <- raw_data |>
          population, party, answer, candidate_name, hypothetical, pct)
 
 #### Save data ####
-write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")
+write_parquet(cleaned_data, "data/02-analysis_data/analysis_data.parquet")
 
 #### Clean data for model####
 # Read the data
-data <- read.csv("data/02-analysis_data/analysis_data.csv")
+data <- read.csv("data/02-analysis_data/analysis_data.parquet")
 
 # Change the form of date
 data$end_date <- mdy(data$end_date)
@@ -41,4 +43,4 @@ data_filtered <- data_filtered %>%
   summarise(average_pct = mean(pct, na.rm = TRUE))
 
 #### Save data ####
-write_csv(data_filtered, "data/02-analysis_data/model_data.csv")
+write_parquet(data_filtered, "data/02-analysis_data/model_data.parquet")

### 2024-11-04 scripts/06-model_data.R
Model data.

@@ -13,13 +13,21 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-data_filtered <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
+data_filtered <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
 data_filtered <- data_filtered %>% mutate(pct = average_pct / 100)
 
 
 ### Model data ####
-model <- glm(pct ~ end_date_numeric + candidate_name, data = data_filtered, 
-             family = binomial(link = "logit"))
+model <- 
+  stan_glm(
+    formula = pct ~ end_date_numeric + candidate_name, 
+    data = data_filtered, 
+    family = gaussian(),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_aux = exponential(rate = 1, autoscale = TRUE),
+    seed = 304
+    )
 summary(model)
 
 

### 2024-11-04 paper/paper.qmd
Update paper.

--- 2024-11-01 paper/paper.qmd
@@
 library(kableExtra)
+library(scales)
+install.packages("arrow")
+library(arrow)
 
-data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
 ```
@@
 # Model
+In this analysis, we utilize a logistic regression model to predict polling percentages for the 2024 U.S.
+presidential candidates over time.
+In order to focus on states with historical significance in elections.
+The model is specified as a Generalized Linear Model (GLM) with a binomial family and a logit link function, appropriate for modeling binary or proportion-based outcomes.
 
 ## Model set-up
+The dataset, model_data.csv, provides polling data with average_pct as the observed average polling percentage among 7 swing states. The end_date indicates the polling period's endpoint.
+To predict polling percentages beyond the available data, we created an additional sequence of 20 days beyond the dataset's last recorded date.
+Because we want to predict the result in November 5.
+This expansion allows for forecasting near-term polling trends.
+Also, capturing potential shifts in candidate support leading up to election day.
+The model was trained on existing data and applied to this extended date range using predict(model, newdata = ., type = "response").
+
+Our model setup and variable selection are as follows:
+$$
+\text{logit}(p_i) = \beta_0 + \beta_1 (\text{Date}) + \beta_2 (\text{Candidate})
+$$
+
+where:
+
+- $$p_i \ \text{represents the probability of support for candidate i at a specific date.}$$
+- $$\beta_0 \ \text{is the intercept, representing baseline support.}$$
+- $$\beta_1 \ \text{captures changes in support over time (date effect).}$$
+- $$\beta_2 \ \text{is a categorical variable accounting for each candidate.}$$
 
 ### Model justification
+The choice of a logistic regression model was guided by the nature of polling data.
+Nature of polling data represents proportions that naturally bound between 0 and 1.
+The logistic function’s S-shaped curve effectively models the relationship between time and polling percentage, accommodating non-linear trends that may arise as election day nears.
+Firstly, candidate names should be included as a categorical predictor in the model.
+It allows us to capture individual impact in support rates by candidate.
+In addition, a transformation from date to numeric is made on end_date in order to get a numerical format.
+It is called the end_date_numeric.
+It helps put date as a predictor in the model.
+By structuring the model this way, it can predict the percentage of the poll by both the impact of candidates and trends over time.
 
@@
   theme(legend.position = "bottom")
+```
+
+## Swing State Polling Prediction Model
+@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.
+```{r}
+#| label: fig-4
+#| fig-cap: "Swing State Polling Prediction Model"
+#| echo: false
+#| warning: false
+#| message: false
+
+invisible(Sys.setlocale("LC_TIME", "en_US"))
+data_filtered <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
+model <- readRDS(here::here("models/model.rds"))
+data_filtered <- data_filtered %>%
+  mutate(predicted_pct = predict(model, newdata = ., type = "response"))
+
+last_date <- max(data_filtered$end_date, na.rm = TRUE)
+new_dates <- seq.Date(from = last_date + 1, by = "day", length.out = 20)
+new_data <- expand.grid(
+  end_date = new_dates,
+  candidate_name = unique(data_filtered$candidate_name)
+)
+new_data <- new_data %>%
+  mutate(
+    end_date_numeric = as.numeric(end_date), 
+  ) %>% mutate(predicted_pct = predict(model, newdata = ., type = "response"))
+all_data <- bind_rows(data_filtered, new_data)
+
+ggplot(all_data, aes(x = end_date, y = pct, color = candidate_name)) +
+  geom_point(aes(y = average_pct/100), alpha = 0.5) + 
+  geom_line(aes(y = predicted_pct), size = 1) + 
+  labs(title = "2024 US President Polls - Predicted vs True",
+       x = "Date",
+       y = "Rate of support") +
+  theme_minimal() +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
+  scale_y_continuous(labels = percent_format(), limits = c(0.44, 0.48))
+
 ```
@@
 This referral incentive taps into snowball sampling, where respondents refer people within their network to participate, expanding our pool of respondents organically.
-However, using snowball sampling in an election survey introduces potential biases, particularly the risk of overrepresentation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies.
+However, using snowball sampling in an election survey introduces potential biases, particularly the risk of over representation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies.
 To mitigate this, we will place specific restrictions on the referral program.

### 2024-11-04 paper/paper.qmd
Merge the paper.

--- 2024-11-04 paper/paper.qmd
@@
 
+\newpage
+
+# Additional data details
+
+# Model details {#sec-model-details}
+
+## Posterior predictive check
+
+```{r}
+
+```
+
+## Diagnostics
+
+```{r}
+
+```
+
+\newpage
+
 # References

### 2024-11-04 paper/paper.qmd
Update paper.

@@
 #| message: false
-
+options(repos = c(CRAN = "https://cloud.r-project.org"))
 library(tidyverse)
@@
 library(arrow)
+library(bayesplot)
+library(rstanarm)
 
@@
 
-# Appendix B
+# Appendix B {-}
 
-##  Idealized Questionnaire and Survey
+#  Idealized Questionnaire and Survey
 
@@
 ```{r}
-
+posterior_predictions <- posterior_predict(model, draws = 100)
+ppc_dens_overlay(y = data_filtered$average_pct/100, yrep = posterior_predictions) +
+  labs(title = "Posterior Predictive Check",
+       x = "Rate of support",
+       y = "Density")
 ```

### 2024-11-04 paper/paper.qmd
Update paper.

@@
 #| message: false
-options(repos = c(CRAN = "https://cloud.r-project.org"))
 library(tidyverse)
@@
 library(scales)
-install.packages("arrow")
 library(arrow)

### 2024-11-04 paper/paper.qmd
update citation

@@
 
-We use the statistical programming language R [@citeR].
+Our analysis was conducted using R [@citeR] along with several supporting packages.
+We used the **tidyverse** for data manipulation [@tidyverse], **readr** for data import [@readr], and **here** for file management [@here].
+
+Dynamic reporting was handled with **knitr** [@knitr], while **kableExtra** allowed for enhanced table formatting [@kableExtra].
+We used **scales** to adjust visualization scales [@scales], and **arrow** for efficient data processing [@arrow].
+
+For Bayesian modeling and visualization, we used **bayesplot** [@bayesplot] and **rstanarm** [@rstanarm].
 

### 2024-11-04 paper/paper.qmd
update model visual

@@
 ```{r}
+#| echo: false
+#| warning: false
+#| message: false
 posterior_predictions <- posterior_predict(model, draws = 100)

### 2024-11-04 paper/paper.qmd
update data section

@@
 # Data {#sec-data}
+The data used in this paper was obtained from the FiveThirtyEight website [@Best2024], which aggregates polling data and other relevant indicators to track the U.S.
+election landscape.
+We accessed this data using custom web scraping tools and APIs provided by FiveThirtyEight.
+The dataset includes information on pollster, state, start and end dates of polls, sample size, population type (e.g., registered voters or likely voters), and party affiliation.
 
 ## Overview
-
 Our analysis was conducted using R [@citeR] along with several supporting packages.
@@
 ## Measurement
+The FiveThirtyEight dataset is updated in real-time, providing the latest polling data for the 2024 U.S.
+presidential election.
+This dataset aggregates information from multiple reputable polling sources, applying adjustments to enhance reliability, such as weighting based on pollster quality and recency of data.
+These measures ensure that the dataset remains a dependable reflection of current voter sentiment and trends as Election Day approaches.
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+## Analysis Data
+The analysis dataset includes several key variables: State, Sample Size, Population Type (e.g., Registered Voters), Party Affiliation, Candidate Preference (Trump or Harris), and Pollster.
+These variables allow for an analysis of voter sentiment in specific swing states, with a focus on support levels between Donald Trump and Kamala Harris.
 
-## Outcome variables
+Certain variables, such as Question ID, Start Date, End Date, and Hypothetical Questions, were removed as they were not necessary for this analysis.
+Additionally, data on other candidates was excluded to concentrate solely on the Trump vs.
+Harris matchup, aligning with the focus on the most relevant contenders in the seven swing states: Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin, Nevada.
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+@tbl-sample provides a random sample of the analysis dataset, displaying all relevant variables used for analysis.
 
 ```{r}
+#| label: tbl-sample
+#| tbl-cap: Random sample of 10 rows from the analysis data.
 #| echo: false
@@
 
-# Set seed for reproducibility
-set.seed(316)
+set.seed(311)
 
-# Sample 10 random observations from the filtered data with Trump and Harris
+# Sample 10 random observations from the filtered data with Trump and Harris, and remove unnecessary columns
 sample_data <- data %>%
   filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
-  sample_n(10)
+  sample_n(10) %>%
+  select(-start_date, -end_date, -question_id, -hypothetical, -pct)
 
-# Display the sampled data as a table with smaller text and adjusted column spacing
+# Display the sampled data as a table with refined styling
 kable(sample_data, caption = "Sample of 10 Random Observations from the Analysis Data") %>%
-  kable_styling(font_size = 8, full_width = FALSE) %>%  # Set full_width to FALSE to center the table
-  column_spec(1:ncol(sample_data), width = "2cm")  # Adjust width as needed, here set to 2cm per column
-
-```
-
-```{r}
+  kable_styling(full_width = FALSE, position = "center") %>%  # Center the table in the PDF
+  column_spec(1, width = "3cm") %>%    # Adjust specific columns for better fit
+  column_spec(2, width = "2.5cm") %>%
+  column_spec(3, extra_css = "padding-left: -5px;") %>%  # Move sample_size column slightly to the left
+  column_spec(4:5, width = "1.5cm")    # Adjust remaining columns with less text
 
@@
 ## Influence of Endorsements and High-Profile Backing
-Recently, high-profile figures like Elon Musk have publicly backed Trump, using their influence to mobilize support for his campaign.
-Musk’s endorsement may energize Trump’s voter base, especially among his followers and individuals interested in business and technology.
-This kind of visible support from influential figures could affect last-minute voter decisions, particularly in tightly contested states where Trump’s lead is slim.
-If Musk’s endorsement translates into increased campaign funding or social media influence, it could bolster Trump’s standing in swing states where the margin remains close, potentially altering the final outcome on November 5th.
+Recently, high-profile figures like Elon Musk have publicly thrown their support behind Trump, leveraging their influence to rally support for his campaign [@Zahn2024].
+Musk’s endorsement could invigorate Trump’s base, especially among Musk’s followers and those engaged in the fields of business and technology.
+This visible backing from such influential figures has the potential to sway undecided voters and influence last-minute decisions, particularly in swing states where Trump’s lead remains narrow.
+
+Musk’s endorsement might not only energize Trump’s existing supporters but could also lead to a boost in campaign funds and social media engagement, further strengthening Trump’s position.
+In closely contested states, where a few thousand votes can make a significant difference, this level of backing from a high-profile figure could be crucial.
+If Musk’s involvement draws in additional resources and amplifies Trump’s visibility, it may ultimately impact the final outcome of the election on November 5th.
 

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Added survey questions and refined appendix.

@@
 Our analysis and prediction utilizes data collected by a single pollster and it is important to scrutinize the sampling methodology behind the sampling methods used to determine the extent of the external validity of our predictions.
-Primarily, the data gathered by New York Times was done so with the collaboration with Siena College through live-interviewers reaching voters by telephone.
+Primarily, the data gathered by New York Times was done so with the collaboration with Sienna College through live-interviewers reaching voters by telephone.
+
+## Target Population and Sampling Frame
 The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
-Consequently, the target population is registered voters of the United States of America and the sampling frame is the national list of registered voters from which NYC employs random sampling to create their pollsters.
-And from this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
+Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters.
+This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information.
+From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
+
+## Recruitment Methods
 The poll relies on random digit dialing to reach voters, predominantly via cell phones.
@@
 This results in their rendition of random sampling, which contributes to the external validity of data.
-However, though the sample was selected randomly, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
+However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
+In fact, according to an article by Emerson College, telephone polling has become entirely obsolete (@EmersonCollege).
 Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling.
@@
 Moreover, voters that are reached over the phone may feel the urge to provide more ‘socially desirable’ responses that are not reflective of their true opinions.
+
+## Non-Response Remedies
 With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics.
@@
 Once the strata are established, respondents are randomly selected within each group, ensuring that all demographic groups are appropriately represented in proportion to their actual distribution within the electorate.
+Furthermore, post-survey weighting is employed to more closely resemble this distribution.
 
@@
 This approach helps to minimize sampling error by ensuring that all significant voter subgroups are included, thus increasing the reliability of the poll’s predictions.
+It is standard practice for them to sample 1,000 respondents for their polls.
+Using stratified sampling to have this sample size closely resemble that of the entire target population cuts costs and provides efficient real-time data.
+
+## Stratified Sampling over Random Sampling
+
+If the methodology randomly sampled from the target population without regard for the distribution of demographics in the state, significant increases to the sample sizes have to be made.
+Random sampling will have largely less precision in representing the distribution of different demographics within a given state unless a large enough sample size were to be drawn.
+Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources.
+With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is (@tellingstorieswithdata).
+As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.
 
@@
 Additionally, while phone polling offers broad geographic reach and a standardized mode of data collection, it limits the sample to voters with phone access who are willing to participate in phone interviews, potentially introducing selection bias if certain demographics are less reachable by phone.
+Although New York Times/Sienna College employs random digit dialing from their sampling frame, their rendition of sample recruitment requires them to sample individuals according to quotas, resulting in nonprobability sampling.
+
+## Evaluation of Questionnaire Design in the Times/Siena Poll
+
+### Strengths
+
+The Times/Siena Poll’s approach to questionnaire design reflects a careful effort to craft unbiased, relevant, and inclusive questions.
+By tailoring questions to current events and topics of widespread interest, the poll aims to capture public sentiment on issues that directly affect voters' attitudes, such as economic conditions or recent political debates.
+This responsiveness to current events strengthens the poll's relevance and allows it to track shifts in opinion over time.
+The poll’s commitment to neutrality is a significant strength.
+Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented.
+The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups (@NewYorkTimes).
+Clarity is also a central focus in their questionnaire development.
+The team emphasizes ensuring that each question is clear and unambiguous, minimizing the risk of misinterpretation.
+This dedication to straightforward, widely understandable questions improves the validity of responses, as it reduces the chance that respondents interpret questions differently based on background or knowledge level.
+
+### Limitations
+
+Despite the strengths of the Times/Siena Poll’s questionnaire design, there are some limitations.
+One notable concern is that, although the poll tries to avoid leading questions, any standardized questionnaire may still unintentionally prime respondents or introduce subtle biases, especially when questions involve sensitive or polarizing topics.
+Although the pollster tries to avoid attrition bias by keeping each interview less than 15 minutes, in seeking to make questions clear and concise, the questionnaire may not capture the full nuance of voter opinions, especially on multifaceted issues like economic policy or social justice.
+While the poll strives to capture real views without introducing new ideas, respondents are still prone to a social desirability bias.
+This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions.
+Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses (@thepsygologyofsurveyresponse)
+
+\newpage
+
+# Appendix B {-}
 
@@
 Assuming New York Times’ 2% voter response rate, to sample 1000 voters, at least 50,000 voters will need to be called.
-It is likely that our team will be dialing way more than 50,000 times since it is an unreasonable assumption that every voter we call would pick up or be available to provide a response.
+It is likely that our team will be dialing abundantly more than 50,000 times since it is an unreasonable assumption that every voter we call would pick up or be available to provide a response.
 There is also the fact that our team does not carry the same credibility and history of acquiring poll data as the New York Times does, resulting in more reluctance for voters to share information with us.
@@
 
-Although weighting adjustments helps  us represent our  target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels.
+Although weighting adjustments helpsus represent our target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels since it will be advertised online.
 To produce accurate predictions of election results, our sample needs to be acquired from a target population that will participate in the election.
@@
 Our survey is divided into three main sections: Preamble, Eligibility, and Party Affiliation.
-The survey we constructed can be found in Appendix B.
 
@@
 
-\newpage
-
-# Appendix B {-}
+# Budget Allocation
+  Advertisements for sampling recruitment: $70,000
+  Prize Pool for Incentive: $5,000
+  Data Processing and Cleaning: $15,000
+  Miscellaneous Expenses: $5,000
+  Petty Cash: $5,000
 
@@
 
+# Structure
+
+## Preamble
+
+Title: 2024 Presidential Election Poll Data
+
+Introduction: Thank you for your participation in our $5,000 giveaway program.
+
+For entry, please complete the survey in its entirety below.
+Please be informed that your answers are strictly confidential and will, under no circumstances, be shared with any party, group, or persons of affiliation.
+
+$5,000 Cash Voucher Program Details: Completing the survey below qualifies as one entry into our giveaway.
+Each participant receives a unique entry identifier, and every entry will have an equal chance in our final random selection of the prize winner.
+Please note that each individual may complete only one survey.
+
+Referral Program: Our referral program offers you the chance to increase your odds of winning.
+After completing the survey, you’ll receive a unique referral code.
+If a friend or associate completes the survey using your code, your total number of entries doubles, effectively doubling your chances of winning the $5,000 prize.
+
+Finally, we wish to clarify that this survey is conducted purely for research purposes and is entirely unaffiliated with any political party, organization, or individual in a position of power.
+Our goal is to gain insight into the evolving political landscape and levels of public engagement.
+
+Referral Code (please ignore if inapplicable)
+
+If you have entered a referral code above, please indicate the relationship with the referee from the best choice below.
+Friend
+Associate
+Relative
+Other…
+
+## Eligibility
+Do you meet your state's residency requirements?
+Yes
+No (End Survey)
+Please select "N/A" from the options below if you reside in North Dakota. 
+Which of the following best describes you?
+I am registered to vote
+I am not registered to vote
+I plan to register
+N/A
+Full Name (For identification of $5,000 cash winner)
+From which state will you be vote for the next president of the United States of America?
+Where can we reach you when we announce the winner?
+E-mail
+Telephone
+Other…
+Contact information
+**We will not use this for any other purpose than to announce winners. It will only be used to reach our lucky winner for instructions on receiving the cash prize.
+Which of the following age groups best describes you?
+18-25
+26-31
+32-40
+41-50
+51-60
+61-80
+81-125
+Under 18
+Which of the following best describes you?
+American Indian or Alaskan Native
+Asian
+African American
+Hispanic or Latino
+Native Hawaiian or Pacific Islander
+White
+Middle Eastern or North African
+Other…
+What is your gender?
+Male
+Female
+Prefer not to say
+Other…
+Which of the following situations best describe you?
+I did not vote in the 2020 presidential election
+I planned to vote but wasn’t able to
+I voted in the 2020 presidential election
+How likely are you to vote in the upcoming election?
+Very unlikely
+1
+2
+3
+Very likely
+Have you attended a presidential rally or their campaigns this year?
+Yes
+No
+Only in the past
+On a scale of 1 to 3, how closely do you follow the presidential race?
+Not at all
+1
+2
+3
+4
+5
+Very closely
+
+## Party Affiliation
+Which party do you prefer a candidate to be chosen from?
+Democratic Party's candidate
+Republican Party's candidate
+Another Party's candidate
+In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
+Donald Trump
+Joe Biden
+Neither
+Other…
+If planning to vote, which presidential candidate are you planning to vote for?
+If you are abstaining, please select which candidate you feel more strongly about.
+Donald Trump
+Kamala Harris
+Other...
 \newpage

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Added in-text citations for appendix.

@@
 The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
-Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters.
+Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters @nyt_poll.
 This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information.
-From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population.
+From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population @nyt_poll.
 
@@
 However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
-In fact, according to an article by Emerson College, telephone polling has become entirely obsolete (@EmersonCollege).
+In fact, according to an article by Emerson College, telephone polling has become entirely obsolete @kimball_polling.
 Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling.
@@
 Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
-Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% (New York Times).
+Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% @nyt_poll.
 
@@
 Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources.
-With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is (@tellingstorieswithdata).
+With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is @tellingstories.
 As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.
@@
 Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented.
-The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups (@NewYorkTimes).
+The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups @nyt_poll.
 Clarity is also a central focus in their questionnaire development.
@@
 This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions.
-Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses (@thepsygologyofsurveyresponse)
+Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses @psychology_survey_response.
 
@@
 
-According to 2024 polling data conducted by New York Times, the swing states are determined to be the following:
+According to 2024 polling data conducted by New York Times, the swing states are determined to be the following @boyce_swing_states:
 
@@
 Other...
+
 \newpage

### 2024-11-04 scripts/01-test_simulated_data.R
update script -> testing

@@ -1,19 +1,16 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: MIT
+# Purpose: Tests the structure and validity of the simulated US election data.
+# Author: Andy Jiang
+# Date: 4 November 2024
+# Contact: ayx.jiang@mail.utoronto.ca
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
 
 #### Workspace setup ####
 library(tidyverse)
 
+# Load the data
 analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
@@ -23,14 +20,13 @@ if (exists("analysis_data")) {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
-
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 200 rows
+if (nrow(analysis_data) == 200) {
+  message("Test Passed: The dataset has 200 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 200 rows.")
 }
 
 # Check if the dataset has 3 columns
@@ -47,19 +43,19 @@ if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
   stop("Test Failed: The 'division' column contains duplicate values.")
 }
 
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
+# Check if the 'state' column contains only valid U.S. state names
+valid_states <- c("Pennsylvania", "Arizona", "Montana", "Florida", "Texas", 
+                  "Nebraska CD-2", "Michigan", "Ohio", "Wisconsin", "Georgia", 
+                  "North Carolina", "Nevada", "Virginia")
 
 if (all(analysis_data$state %in% valid_states)) {
[…]

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -1,69 +1,44 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests analysis data
+# Author: Andy Jiang
+# Date: 4 November 2024
+# Contact: ayx.jiang@mail.utoronto.ca
+# Pre-requisites: cleaned the raw data
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(arrow)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
+# Load the cleaned data from the specified data folder
+cleaned_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+
+# Test that the dataset only includes the seven swing states
+test_that("dataset includes only selected swing states", {
+  swing_states <- c("Pennsylvania", "Georgia", "North Carolina", 
+                    "Michigan", "Arizona", "Wisconsin", "Nevada")
+  expect_true(all(cleaned_data$state %in% swing_states))
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+# Test that the dataset contains no missing values
+test_that("dataset has no missing values", {
+  expect_true(all(!is.na(cleaned_data)))
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
+# Test that the `population` column contains only "rv" entries
+test_that("population column contains only 'rv'", {
+  expect_true(all(cleaned_data$population == "rv"))
 })
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
+# Test that the `candidate_name` column includes at least two candidates
+test_that("candidate_name column has at least two unique candidates", {
+  expect_true(length(unique(cleaned_data$candidate_name)) >= 2)
 })
 
[…]

### 2024-11-04 scripts/03-clean_data.R
Clean data.

@@ -27,7 +27,7 @@ write_parquet(cleaned_data, "data/02-analysis_data/analysis_data.parquet")
 
 #### Clean data for model####
 # Read the data
-data <- read.csv("data/02-analysis_data/analysis_data.parquet")
+data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 # Change the form of date
 data$end_date <- mdy(data$end_date)
@@ -42,5 +42,7 @@ data_filtered <- data_filtered %>%
   group_by(end_date_numeric, candidate_name, end_date)%>% 
   summarise(average_pct = mean(pct, na.rm = TRUE))
 
+data_filtered <- data_filtered %>% mutate(pct = average_pct / 100)
+
 #### Save data ####
-write_parquet(data_filtered, "data/02-analysis_data/model_data.parquet")
+write_csv(data_filtered, "data/02-analysis_data/model_data.csv")

### 2024-11-04 scripts/06-model_data.R
Model data.

@@ -13,10 +13,7 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-data_filtered <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
-data_filtered <- data_filtered %>% mutate(pct = average_pct / 100)
-
-
+data_filtered <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
 ### Model data ####
 model <- 
   stan_glm(

### 2024-11-04 paper/paper.qmd
Update paper.

--- 2024-11-04 paper/paper.qmd
@@
 library(rstanarm)
-
+data_filtered <- read.csv(here::here("data/02-analysis_data/model_data.csv"))
 data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
@@
 # Data {#sec-data}
-The data used in this paper was obtained from the FiveThirtyEight website [@Best2024], which aggregates polling data and other relevant indicators to track the U.S.
-election landscape.
-We accessed this data using custom web scraping tools and APIs provided by FiveThirtyEight.
-The dataset includes information on pollster, state, start and end dates of polls, sample size, population type (e.g., registered voters or likely voters), and party affiliation.
 
 ## Overview
-Our analysis was conducted using R [@citeR] along with several supporting packages.
-We used the **tidyverse** for data manipulation [@tidyverse], **readr** for data import [@readr], and **here** for file management [@here].
 
-Dynamic reporting was handled with **knitr** [@knitr], while **kableExtra** allowed for enhanced table formatting [@kableExtra].
-We used **scales** to adjust visualization scales [@scales], and **arrow** for efficient data processing [@arrow].
-
-For Bayesian modeling and visualization, we used **bayesplot** [@bayesplot] and **rstanarm** [@rstanarm].
+We use the statistical programming language R [@citeR].
 
 ## Measurement
-The FiveThirtyEight dataset is updated in real-time, providing the latest polling data for the 2024 U.S.
-presidential election.
-This dataset aggregates information from multiple reputable polling sources, applying adjustments to enhance reliability, such as weighting based on pollster quality and recency of data.
-These measures ensure that the dataset remains a dependable reflection of current voter sentiment and trends as Election Day approaches.
 
-## Analysis Data
-The analysis dataset includes several key variables: State, Sample Size, Population Type (e.g., Registered Voters), Party Affiliation, Candidate Preference (Trump or Harris), and Pollster.
-These variables allow for an analysis of voter sentiment in specific swing states, with a focus on support levels between Donald Trump and Kamala Harris.
+Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
 
-Certain variables, such as Question ID, Start Date, End Date, and Hypothetical Questions, were removed as they were not necessary for this analysis.
-Additionally, data on other candidates was excluded to concentrate solely on the Trump vs.
-Harris matchup, aligning with the focus on the most relevant contenders in the seven swing states: Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin, Nevada.
+## Outcome variables
 
-@tbl-sample provides a random sample of the analysis dataset, displaying all relevant variables used for analysis.
+Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
 
 ```{r}
-#| label: tbl-sample
-#| tbl-cap: Random sample of 10 rows from the analysis data.
 #| echo: false
@@
 
-set.seed(311)
+# Set seed for reproducibility
+set.seed(316)
 
-# Sample 10 random observations from the filtered data with Trump and Harris, and remove unnecessary columns
+# Sample 10 random observations from the filtered data with Trump and Harris
 sample_data <- data %>%
   filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
-  sample_n(10) %>%
-  select(-start_date, -end_date, -question_id, -hypothetical, -pct)
+  sample_n(10)
 
-# Display the sampled data as a table with refined styling
+# Display the sampled data as a table with smaller text and adjusted column spacing
 kable(sample_data, caption = "Sample of 10 Random Observations from the Analysis Data") %>%
-  kable_styling(full_width = FALSE, position = "center") %>%  # Center the table in the PDF
-  column_spec(1, width = "3cm") %>%    # Adjust specific columns for better fit
-  column_spec(2, width = "2.5cm") %>%
-  column_spec(3, extra_css = "padding-left: -5px;") %>%  # Move sample_size column slightly to the left
-  column_spec(4:5, width = "1.5cm")    # Adjust remaining columns with less text
+  kable_styling(font_size = 8, full_width = FALSE) %>%  # Set full_width to FALSE to center the table
+  column_spec(1:ncol(sample_data), width = "2cm")  # Adjust width as needed, here set to 2cm per column
+
+```
+
+```{r}
 
@@
 ## Swing State Polling Prediction Model
-@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.
+@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Donald Trump may win based on our model.
 ```{r}
@@
 invisible(Sys.setlocale("LC_TIME", "en_US"))
-data_filtered <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
+model_data <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
 model <- readRDS(here::here("models/model.rds"))
-data_filtered <- data_filtered %>%
+
+model_data <- model_data %>%
   mutate(predicted_pct = predict(model, newdata = ., type = "response"))
-
-last_date <- max(data_filtered$end_date, na.rm = TRUE)
+last_date <- max(model_data$end_date, na.rm = TRUE)
 new_dates <- seq.Date(from = last_date + 1, by = "day", length.out = 20)
@@
   end_date = new_dates,
-  candidate_name = unique(data_filtered$candidate_name)
+  candidate_name = unique(model_data$candidate_name)
 )
@@
   ) %>% mutate(predicted_pct = predict(model, newdata = ., type = "response"))
-all_data <- bind_rows(data_filtered, new_data)
+all_data <- bind_rows(model_data, new_data)
 
@@
 ## Influence of Endorsements and High-Profile Backing
-Recently, high-profile figures like Elon Musk have publicly thrown their support behind Trump, leveraging their influence to rally support for his campaign [@Zahn2024].
-Musk’s endorsement could invigorate Trump’s base, especially among Musk’s followers and those engaged in the fields of business and technology.
-This visible backing from such influential figures has the potential to sway undecided voters and influence last-minute decisions, particularly in swing states where Trump’s lead remains narrow.
-
-Musk’s endorsement might not only energize Trump’s existing supporters but could also lead to a boost in campaign funds and social media engagement, further strengthening Trump’s position.
-In closely contested states, where a few thousand votes can make a significant difference, this level of backing from a high-profile figure could be crucial.
-If Musk’s involvement draws in additional resources and amplifies Trump’s visibility, it may ultimately impact the final outcome of the election on November 5th.
+Recently, high-profile figures like Elon Musk have publicly backed Trump, using their influence to mobilize support for his campaign.
+Musk’s endorsement may energize Trump’s voter base, especially among his followers and individuals interested in business and technology.
+This kind of visible support from influential figures could affect last-minute voter decisions, particularly in tightly contested states where Trump’s lead is slim.
+If Musk’s endorsement translates into increased campaign funding or social media influence, it could bolster Trump’s standing in swing states where the margin remains close, potentially altering the final outcome on November 5th.
 
@@
 
+\newpage
+
 # Model details {#sec-model-details}
@@
 
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
+This shows that the posterior predictive density closely follows the observed data density.
+Discrepancies between the two suggest that the model may be missing some aspect of the data structure or variability, which could guide potential model adjustments or refinement.
+
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
+This shows the prior for each parameter is centered around zero, but the posterior shows more precise estimates for each candidate and the date variable, reflecting the data's influence.
+Also, the posterior narrowing suggests that the model successfully extracted information from the data, reducing uncertainty around parameter estimates compared to the prior.
+model_data <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
+
 ```{r}
+#| eval: true
 #| echo: false
+#| message: false
 #| warning: false
-#| message: false
-posterior_predictions <- posterior_predict(model, draws = 100)
-ppc_dens_overlay(y = data_filtered$average_pct/100, yrep = posterior_predictions) +
-  labs(title = "Posterior Predictive Check",
-       x = "Rate of support",
-       y = "Density")
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+pp_check(model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
 ```
@@
 
+@fig-stanareyouokay-1 is a trace plot.
+It shows chain mixing, stationarity and no drifting.
+This suggests that the model's MCMC sampling achieved convergence for each parameter.
+The chains are well-mixed and stationary, providing confidence in the posterior estimates derived from this sampling process.
+
+@fig-stanareyouokay-2 is a Rhat plot.
+It shows the Rhat values for the parameters estimated in the model.
+Values close to 1 indicate that the chains have mixed well and the posterior distribution has been adequately explored.
+This suggests that the model has converged successfully and the estimates are reliable for inference.
+
 ```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
 
+plot(model, "trace")
+
+plot(model, "rhat")
 ```

### 2024-11-04 paper/paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 
+>>>>>>> cadfff05ead6aebff23ab03f96847c7f519121a6
 # Idealized Methodology
@@
 
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
+This shows that the posterior predictive density closely follows the observed data density.
+Discrepancies between the two suggest that the model may be missing some aspect of the data structure or variability, which could guide potential model adjustments or refinement.
+
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
+This shows the prior for each parameter is centered around zero, but the posterior shows more precise estimates for each candidate and the date variable, reflecting the data's influence.
+Also, the posterior narrowing suggests that the model successfully extracted information from the data, reducing uncertainty around parameter estimates compared to the prior.
+model_data <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
+
 ```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+pp_check(model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
 #| echo: false

### 2024-11-04 paper/paper.qmd
Debug

@@
 where:
-
 - $$p_i \ \text{represents the probability of support for candidate i at a specific date.}$$
@@
 # Appendix B {-}
-
->>>>>>> cadfff05ead6aebff23ab03f96847c7f519121a6
-# Idealized Methodology
 

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Interpreted results more clearly and organized the structure of results section.

@@
 When looking at the overall average across these states, Harris slightly edges out Trump, indicating her overall advantage in these swing areas.
-
-## Polling Percentage Distribution
-The box plot in @fig-2 demonstrates the range and consistency of support for both candidates across each state.
-Trump shows a wider range of support, reflecting variability, while Harris has relatively steady polling percentages across states, maintaining higher consistency.
-Harris’s support is less variable and generally centers around higher polling percentages compared to Trump’s.
-
-## Difference in Average Polling Percentage
-@fig-3 highlights the difference in average polling percentages by state, with positive values indicating Trump’s lead and negative values indicating Harris's.
-Trump’s lead in the three states (Arizona, Georgia, and North Carolina) is relatively narrow, with margins of less than 1 percent.
-In contrast, Harris’s lead in the states favoring her (Pennsylvania, Wisconsin, Nevada, and Michigan) ranges from 1 to 4 percent, indicating her stronger support in the states where she leads.
+In our assumed electoral map, this projects Kamala Harris over the edge with 276 electoral votes as opposed to Donald Trump's 262.
+This shows that our model predicts Kamala Harris to win the 2024 Presidential Election if she is able to maintain her lead over all of Pennsylvania, Wisconsin, Nevada, and Michigan.
 
@@
 ```
+## Polling Percentage Distribution
+The box plot in @fig-2 demonstrates the range and consistency of support for both candidates across each state.
+Trump shows a wider range of support, reflecting variability, while Harris has relatively steady polling percentages across states, maintaining higher consistency.
+Harris’s support is less variable and generally centers around higher polling percentages compared to Trump’s.
 
@@
 ```
+## Difference in Average Polling Percentage
+@fig-3 highlights the difference in average polling percentages by state, with positive values indicating Trump’s lead and negative values indicating Harris's.
+Trump’s lead in the three states (Pennsylvania, Wisconsin, Nevada, and Michigan) is relatively narrow, with margins of less than 1 percent.
+In contrast, Harris’s lead in the states favoring her (Pennsylvania, Wisconsin, Nevada, and Michigan) ranges from 1 to 4 percent, indicating her stronger support in the states where she leads.
+Consequently, this difference in average polling percentages show that Kamala Harris' lead of 276 electoral votes is supported by a reliable margin and Donald Trump's lead in Arizona, Georgia, and North Carolina is turbulent.
+
 ```{r}
@@
 ## Swing State Polling Prediction Model
-@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Donald Trump may win based on our model.
+However, @fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the days until the election.
+This support rate changes model exhibits a higher rate of growth in Donald Trump's share of support.
+Although Kamala Harris is in the lead, Donald Trump's growth of support rate is an element that could stifle Harris' lead and drop her below her required 270 electoral votes.
 ```{r}
@@
 # Discussion
+## Turbulent Margins
+Based on our results from @fig-1 predicted that Kamala Harris to win the presidential election with 276 electoral votes.
+Furthermore, @fig-2 showed that her lead in the states of Pennsylvania, Wisconsin, Nevada, and Michigan are stronger than Donald Trump's support in Pennsylvania, Wisconsin, Nevada, and Michigan.
+From @fig-2, we can also observe that Kamala Harris' lead in Nevada seems to be the weakest.
+In the framework of the electoral college system, losing Nevada to Donald Trump would not change the results as Nevada holds 6 electoral votes, which means that Kamala Harris would still possess the necessary 270 to win the election.
+However, this is not the case if Kamala Harris loses support in any of the three other states of Pennsylvania, Wisconsin, and Michigan as this would place her beneath the 270 seat threshold.
+In fact, losing any one of these states would result in Donald Trump's victory.
+@fig-3 showed that the support rate of Donald Trump is increasing faster than that of Kamala Harris', threatening Harris' lead over Pennsylvania, Wisconsin, and Michigan.
 

### 2024-11-04 scripts/03-clean_data.R
Update Clean data.

@@ -9,7 +9,6 @@
 
 #### Workspace setup ####
 library(tidyverse)
-install.packages("arrow")
 library(arrow)
 
 #### Clean data ####
@@ -34,13 +33,12 @@ data$end_date <- mdy(data$end_date)
 data_filtered <- data %>%
   mutate(end_date_numeric = as.numeric(end_date))
 
-# Selct the true polls
-data_filtered <- data_filtered %>%
-  filter(hypothetical == FALSE, !is.na(sample_size))
-
+# Calculate the average pct
 data_filtered <- data_filtered %>% 
-  group_by(end_date_numeric, candidate_name, end_date)%>% 
-  summarise(average_pct = mean(pct, na.rm = TRUE))
+  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
+  group_by(candidate_name, end_date_numeric, end_date) %>%
+  summarize(average_pct = mean(pct, na.rm = TRUE)) %>%
+  mutate(state = " Overall")
 
 data_filtered <- data_filtered %>% mutate(pct = average_pct / 100)
 

### 2024-11-04 paper/paper.qmd
Update the paper.

--- 2024-11-04 paper/paper.qmd
@@
 ## Predictor variables
+End date numeric:
+This variable represents the numeric conversion of the poll end date, indicating the time at which the polling data was collected.
+By transforming dates into numeric values, we can account for temporal trends and shifts in voter sentiment.
+This predictor helps identify changes in support over time and captures any momentum shifts that occur as the election draws closer.
+
+Candidate name:
+This categorical variable distinguishes between the main candidates: Donald Trump and Kamala Harris.
+By including candidate-specific factors, the model can account for differences in support levels attributed to individual characteristics or public perception of each candidate.
+Additionally, this variable enables the model to gauge the relative standing between the two contenders in different states and overall.
 
@@
 ## Swing State Polling Prediction Model
-@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Donald Trump may win based on our model.
+@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Kamala Harris may win based on our model.
 ```{r}
@@
   theme_minimal() +
-  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
-  scale_y_continuous(labels = percent_format(), limits = c(0.44, 0.48))
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", 
+               limits = as.Date(c("2024-01-01", "2024-11-5"))) +
+  scale_y_continuous(labels = percent_format(), limits = c(0.44, 0.47))
 

### 2024-11-04 paper/paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 ## Swing State Polling Prediction Model
-However, @fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the days until the election.
+
+@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Kamala Harris may win based on our model.
+However, this shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the days until the election.
 This support rate changes model exhibits a higher rate of growth in Donald Trump's share of support.
 Although Kamala Harris is in the lead, Donald Trump's growth of support rate is an element that could stifle Harris' lead and drop her below her required 270 electoral votes.
+
 ```{r}

### 2024-11-04 paper/paper.tex

--- 2024-11-04 paper/paper.qmd
@@
----
-title: "Forecasting the 2024 U.S. Presidential Election"
-subtitle: "Using Aggregated Polling Data to Predict the Outcome of the 2024 Presidential Race"
-author: 
-  - Andy Jiang
-  - Onon Burentuvshin
-  - Rui Hu
-thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/president-polls)."
-date: today
-date-format: long
-abstract: "The 2024 U.S.
-presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome.
-This paper aims to build a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election.
-The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions.
-Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process.
-The paper concludes with an idealized polling methodology, designed within a $100K budget, to enhance the accuracy of election forecasts.
-Results are presented in the context of understanding polling trends, potential biases, and the evolving landscape of voter preferences as the election approaches."
-format: pdf
-number-sections: true
-bibliography: references.bib
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-library(tidyverse)
-library(readr)
-library(here)
-library(knitr)
-library(kableExtra)
-library(scales)
-library(arrow)
-library(bayesplot)
-library(rstanarm)
-data_filtered <- read.csv(here::here("data/02-analysis_data/model_data.csv"))
-data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
-```
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-# Introduction
-The 2024 U.S.
-presidential election is shaping up to be one of the most closely watched and potentially pivotal elections in recent history.
-As public opinion shifts and political dynamics evolve, polling data has emerged as a critical tool for forecasting the outcome and understanding voter preferences.
-Polls provide a snapshot of where candidates stand at various points in time, reflecting the impact of campaigns, debates, and major events.
-However, the reliability and accuracy of individual polls can vary significantly based on methodology, sample size, and other factors, making it necessary to aggregate multiple sources of data for a more robust prediction.
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-This paper aims to forecast the outcome of the 2024 U.S.
-presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race.
-By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion.
-Additionally, the paper examines the methodologies of different pollsters to assess their strengths and weaknesses, which can help identify possible biases in the aggregated data.
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Forecasting the 2024 U.S. Presidential Election},
+  pdfauthor={Andy Jiang; Onon Burentuvshin; Rui Hu},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-The analysis will further explore the geographic distribution of support across key swing states, providing insights into the electoral landscape.
-Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts.
-By integrating multiple data sources and critically evaluating polling practices, this study aims to contribute to the ongoing discussion on the role of polling in democratic processes and election forecasting.
+\title{Forecasting the 2024 U.S. Presidential Election\thanks{Code and
+data are available at:
+{[}https://github.com/AndyYanxunJiang/president-polls).}}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{Using Aggregated Polling Data to Predict the Outcome of the
+2024 Presidential Race}
+\author{Andy Jiang \and Onon Burentuvshin \and Rui Hu}
+\date{November 4, 2024}
 
-# Data {#sec-data}
-The data used in this paper was obtained from the FiveThirtyEight website [@Best2024], which aggregates polling data and other relevant indicators to track the U.S.
-election landscape.
-We accessed this data using custom web scraping tools and APIs provided by FiveThirtyEight.
-The dataset includes information on pollster, state, start and end dates of polls, sample size, population type (e.g., registered voters or likely voters), and party affiliation.
+\begin{document}
+\maketitle
+\begin{abstract}
+The 2024 U.S. presidential election is shaping up to be a highly swing
+race, with polling data playing a crucial role in gauging public
+sentiment and forecasting the potential outcome. This paper aims to
+build a predictive model using a poll-of-polls approach, aggregating
+data from multiple pollsters to forecast the winner of the upcoming
+election. The analysis incorporates polling data from various sources,
+filtered to include only high-quality pollsters with a numeric grade
+above 3, to ensure the reliability of the predictions. Additionally, a
+detailed examination of one selected pollster's methodology is
+conducted, highlighting strengths, weaknesses, and biases in the survey
+process. The paper concludes with an idealized polling methodology,
+designed within a \$100K budget, to enhance the accuracy of election
+forecasts. Results are presented in the context of understanding polling
+trends, potential biases, and the evolving landscape of voter
+preferences as the election approaches.
+\end{abstract}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
-## Overview
-Our analysis was conducted using R [@citeR] along with several supporting packages.
-We used the **tidyverse** for data manipulation [@tidyverse], **readr** for data import [@readr], and **here** for file management [@here].
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Dynamic reporting was handled with **knitr** [@knitr], while **kableExtra** allowed for enhanced table formatting [@kableExtra].
-We used **scales** to adjust visualization scales [@scales], and **arrow** for efficient data processing [@arrow].
+The 2024 U.S. presidential election is shaping up to be one of the most
+closely watched and potentially pivotal elections in recent history. As
+public opinion shifts and political dynamics evolve, polling data has
+emerged as a critical tool for forecasting the outcome and understanding
+voter preferences. Polls provide a snapshot of where candidates stand at
+various points in time, reflecting the impact of campaigns, debates, and
+major events. However, the reliability and accuracy of individual polls
+can vary significantly based on methodology, sample size, and other
+factors, making it necessary to aggregate multiple sources of data for a
+more robust prediction.
 
-For Bayesian modeling and visualization, we used **bayesplot** [@bayesplot] and **rstanarm** [@rstanarm].
+This paper aims to forecast the outcome of the 2024 U.S. presidential
+election by leveraging a ``poll-of-polls'' approach, which aggregates
+data from various pollsters to create a more comprehensive picture of
+the race. By focusing on high-quality polls and conducting a detailed
+analysis of the polling trends for the two main candidates, Donald Trump
+and Kamala Harris, we seek to uncover patterns in voter support and
+potential factors influencing shifts in public opinion. Additionally,
+the paper examines the methodologies of different pollsters to assess
+their strengths and weaknesses, which can help identify possible biases
+in the aggregated data.
 
-## Measurement
-The FiveThirtyEight dataset is updated in real-time, providing the latest polling data for the 2024 U.S.
-presidential election.
-This dataset aggregates information from multiple reputable polling sources, applying adjustments to enhance reliability, such as weighting based on pollster quality and recency of data.
-These measures ensure that the dataset remains a dependable reflection of current voter sentiment and trends as Election Day approaches.
+The analysis will further explore the geographic distribution of support
+across key swing states, providing insights into the electoral
+landscape. Finally, the paper presents an idealized polling methodology
+with a \$100,000 budget, designed to improve the accuracy and
+representativeness of election forecasts. By integrating multiple data
+sources and critically evaluating polling practices, this study aims to
+contribute to the ongoing discussion on the role of polling in
+democratic processes and election forecasting.
 
-## Analysis Data
-The analysis dataset includes several key variables: State, Sample Size, Population Type (e.g., Registered Voters), Party Affiliation, Candidate Preference (Trump or Harris), and Pollster.
-These variables allow for an analysis of voter sentiment in specific swing states, with a focus on support levels between Donald Trump and Kamala Harris.
+\hypertarget{sec-data}{%
+\section{Data}\label{sec-data}}
 
-Certain variables, such as Question ID, Start Date, End Date, and Hypothetical Questions, were removed as they were not necessary for this analysis.
-Additionally, data on other candidates was excluded to concentrate solely on the Trump vs.
-Harris matchup, aligning with the focus on the most relevant contenders in the seven swing states: Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin, Nevada.
+The data used in this paper was obtained from the FiveThirtyEight
+website (Best, Bycoffe, et al. 2024), which aggregates polling data and
+other relevant indicators to track the U.S. election landscape. We
+accessed this data using custom web scraping tools and APIs provided by
+FiveThirtyEight. The dataset includes information on pollster, state,
+start and end dates of polls, sample size, population type (e.g.,
+registered voters or likely voters), and party affiliation.
 
-@tbl-sample provides a random sample of the analysis dataset, displaying all relevant variables used for analysis.
+\hypertarget{overview}{%
+\subsection{Overview}\label{overview}}
 
-```{r}
-#| label: tbl-sample
-#| tbl-cap: Random sample of 10 rows from the analysis data.
-#| echo: false
-#| warning: false
-#| message: false
+Our analysis was conducted using R (R Core Team 2022) along with several
+supporting packages. We used the \textbf{tidyverse} for data
+manipulation (Wickham et al. 2019), \textbf{readr} for data import
+(Wickham, Hester, and Bryan 2023), and \textbf{here} for file management
+(Müller 2020).
 
-set.seed(311)
+Dynamic reporting was handled with \textbf{knitr} (Xie 2024), while
+\textbf{kableExtra} allowed for enhanced table formatting (Zhu 2024). We
+used \textbf{scales} to adjust visualization scales (Wickham, Pedersen,
+and Seidel 2023), and \textbf{arrow} for efficient data processing
+(Richardson et al. 2024).
 
-# Sample 10 random observations from the filtered data with Trump and Harris, and remove unnecessary columns
-sample_data <- data %>%
-  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
-  sample_n(10) %>%
-  select(-start_date, -end_date, -question_id, -hypothetical, -pct)
+For Bayesian modeling and visualization, we used \textbf{bayesplot}
+(Gabry and Mahr 2024) and \textbf{rstanarm} (Goodrich et al. 2024).
 
-# Display the sampled data as a table with refined styling
-kable(sample_data, caption = "Sample of 10 Random Observations from the Analysis Data") %>%
-  kable_styling(full_width = FALSE, position = "center") %>%  # Center the table in the PDF
-  column_spec(1, width = "3cm") %>%    # Adjust specific columns for better fit
-  column_spec(2, width = "2.5cm") %>%
-  column_spec(3, extra_css = "padding-left: -5px;") %>%  # Move sample_size column slightly to the left
-  column_spec(4:5, width = "1.5cm")    # Adjust remaining columns with less text
+\hypertarget{measurement}{%
+\subsection{Measurement}\label{measurement}}
 
-```
+The FiveThirtyEight dataset is updated in real-time, providing the
+latest polling data for the 2024 U.S. presidential election. This
+dataset aggregates information from multiple reputable polling sources,
+applying adjustments to enhance reliability, such as weighting based on
+pollster quality and recency of data. These measures ensure that the
+dataset remains a dependable reflection of current voter sentiment and
+trends as Election Day approaches.
 
-## Predictor variables
-End date numeric:
-This variable represents the numeric conversion of the poll end date, indicating the time at which the polling data was collected.
-By transforming dates into numeric values, we can account for temporal trends and shifts in voter sentiment.
-This predictor helps identify changes in support over time and captures any momentum shifts that occur as the election draws closer.
+\hypertarget{analysis-data}{%
+\subsection{Analysis Data}\label{analysis-data}}
 
-Candidate name:
-This categorical variable distinguishes between the main candidates: Donald Trump and Kamala Harris.
-By including candidate-specific factors, the model can account for differences in support levels attributed to individual characteristics or public perception of each candidate.
-Additionally, this variable enables the model to gauge the relative standing between the two contenders in different states and overall.
+The analysis dataset includes several key variables: State, Sample Size,
+Population Type (e.g., Registered Voters), Party Affiliation, Candidate
+Preference (Trump or Harris), and Pollster. These variables allow for an
+analysis of voter sentiment in specific swing states, with a focus on
+support levels between Donald Trump and Kamala Harris.
 
-# Model
-In this analysis, we utilize a logistic regression model to predict polling percentages for the 2024 U.S.
-presidential candidates over time.
+Certain variables, such as Question ID, Start Date, End Date, and
+Hypothetical Questions, were removed as they were not necessary for this
+analysis. Additionally, data on other candidates was excluded to
+concentrate solely on the Trump vs.~Harris matchup, aligning with the
+focus on the most relevant contenders in the seven swing states:
+Pennsylvania, Georgia, North Carolina, Michigan, Arizona, Wisconsin,
+Nevada.
+
+Table~\ref{tbl-sample} provides a random sample of the analysis dataset,
+displaying all relevant variables used for analysis.
+
+\hypertarget{tbl-sample}{}
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{2.5cm}>{}r>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{1.5cm}ll}
+\caption{\label{tbl-sample}Random sample of 10 rows from the analysis data. }Sample of 10 Random Observations from the Analysis Data}\\
+\toprule
+pollster & state & sample\_size & population & party & answer & candidate\_name\\
+\midrule
+PPP & Arizona & 596 & rv & REP & Trump & Donald Trump\\
+Morning Consult & Wisconsin & 700 & rv & REP & Trump & Donald Trump\\
+Morning Consult & Georgia & 800 & rv & REP & Trump & Donald Trump\\
+Morning Consult & Nevada & 574 & rv & REP & Trump & Donald Trump\\
+Bullfinch & Pennsylvania & 800 & rv & DEM & Harris & Kamala Harris\\
+\addlinespace
+Public Opinion Strategies & Pennsylvania & 500 & rv & REP & Trump & Donald Trump\\
+High Point University & North Carolina & 804 & rv & REP & Trump & Donald Trump\\
+Emerson & Michigan & 1000 & rv & REP & Trump & Donald Trump\\
+Quinnipiac & Georgia & 1203 & rv & REP & Trump & Donald Trump\\
+Emerson & Pennsylvania & 850 & rv & REP & Trump & Donald Trump\\
+\bottomrule
+\end{longtable}
+
+\hypertarget{predictor-variables}{%
+\subsection{Predictor variables}\label{predictor-variables}}
+
+\hypertarget{model}{%
+\section{Model}\label{model}}
+
+In this analysis, we utilize a logistic regression model to predict
+polling percentages for the 2024 U.S. presidential candidates over time.
 In order to focus on states with historical significance in elections.
-The model is specified as a Generalized Linear Model (GLM) with a binomial family and a logit link function, appropriate for modeling binary or proportion-based outcomes.
+The model is specified as a Generalized Linear Model (GLM) with a
+binomial family and a logit link function, appropriate for modeling
+binary or proportion-based outcomes.
 
-## Model set-up
-The dataset, model_data.csv, provides polling data with average_pct as the observed average polling percentage among 7 swing states. The end_date indicates the polling period's endpoint.
-To predict polling percentages beyond the available data, we created an additional sequence of 20 days beyond the dataset's last recorded date.
-Because we want to predict the result in November 5.
-This expansion allows for forecasting near-term polling trends.
-Also, capturing potential shifts in candidate support leading up to election day.
-The model was trained on existing data and applied to this extended date range using predict(model, newdata = ., type = "response").
+\hypertarget{model-set-up}{%
+\subsection{Model set-up}\label{model-set-up}}
 
-Our model setup and variable selection are as follows:
-$$
+The dataset, model\_data.csv, provides polling data with average\_pct as
+the observed average polling percentage among 7 swing states. The
+end\_date indicates the polling period's endpoint. To predict polling
+percentages beyond the available data, we created an additional sequence
+of 20 days beyond the dataset's last recorded date. Because we want to
+predict the result in November 5. This expansion allows for forecasting
+near-term polling trends. Also, capturing potential shifts in candidate
+support leading up to election day. The model was trained on existing
+data and applied to this extended date range using predict(model,
+newdata = ., type = ``response'').
+
+Our model setup and variable selection are as follows: \[
 \text{logit}(p_i) = \beta_0 + \beta_1 (\text{Date}) + \beta_2 (\text{Candidate})
-$$
+\]
 
-where:
-- $$p_i \ \text{represents the probability of support for candidate i at a specific date.}$$
-- $$\beta_0 \ \text{is the intercept, representing baseline support.}$$
-- $$\beta_1 \ \text{captures changes in support over time (date effect).}$$
-- $$\beta_2 \ \text{is a categorical variable accounting for each candidate.}$$
+where: -
+\[p_i \ \text{represents the probability of support for candidate i at a specific date.}\]
+- \[\beta_0 \ \text{is the intercept, representing baseline support.}\]
+-
+\[\beta_1 \ \text{captures changes in support over time (date effect).}\]
+-
+\[\beta_2 \ \text{is a categorical variable accounting for each candidate.}\]
 
-### Model justification
-The choice of a logistic regression model was guided by the nature of polling data.
-Nature of polling data represents proportions that naturally bound between 0 and 1.
-The logistic function’s S-shaped curve effectively models the relationship between time and polling percentage, accommodating non-linear trends that may arise as election day nears.
-Firstly, candidate names should be included as a categorical predictor in the model.
-It allows us to capture individual impact in support rates by candidate.
-In addition, a transformation from date to numeric is made on end_date in order to get a numerical format.
-It is called the end_date_numeric.
-It helps put date as a predictor in the model.
-By structuring the model this way, it can predict the percentage of the poll by both the impact of candidates and trends over time.
+\hypertarget{model-justification}{%
+\subsubsection{Model justification}\label{model-justification}}
 
-# Results
+The choice of a logistic regression model was guided by the nature of
+polling data. Nature of polling data represents proportions that
+naturally bound between 0 and 1. The logistic function's S-shaped curve
+effectively models the relationship between time and polling percentage,
+accommodating non-linear trends that may arise as election day nears.
+Firstly, candidate names should be included as a categorical predictor
+in the model. It allows us to capture individual impact in support rates
+by candidate. In addition, a transformation from date to numeric is made
+on end\_date in order to get a numerical format. It is called the
+end\_date\_numeric. It helps put date as a predictor in the model. By
+structuring the model this way, it can predict the percentage of the
+poll by both the impact of candidates and trends over time.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
 The analysis of polling data across key swing states for the 2024 U.S.
-Presidential Election reveals insights into the levels of support for candidates Donald Trump and Kamala Harris.
-The findings are presented through three primary visualizations: the average polling percentage by state, the distribution of polling percentages, and the difference in average polling percentage between the two candidates.
+Presidential Election reveals insights into the levels of support for
+candidates Donald Trump and Kamala Harris. The findings are presented
+through three primary visualizations: the average polling percentage by
+state, the distribution of polling percentages, and the difference in
+average polling percentage between the two candidates.
 
-## Average Polling Percentage by State
-From @fig-1, we can see that in the swing states of Arizona, Georgia, and North Carolina, Trump holds a narrow lead.
-In contrast, Harris leads in Pennsylvania, Wisconsin, Nevada, and Michigan.
-When looking at the overall average across these states, Harris slightly edges out Trump, indicating her overall advantage in these swing areas.
+\hypertarget{average-polling-percentage-by-state}{%
+\subsection{Average Polling Percentage by
+State}\label{average-polling-percentage-by-state}}
 
-## Polling Percentage Distribution
-The box plot in @fig-2 demonstrates the range and consistency of support for both candidates across each state.
-Trump shows a wider range of support, reflecting variability, while Harris has relatively steady polling percentages across states, maintaining higher consistency.
-Harris’s support is less variable and generally centers around higher polling percentages compared to Trump’s.
+From Figure~\ref{fig-1}, we can see that in the swing states of Arizona,
+Georgia, and North Carolina, Trump holds a narrow lead. In contrast,
+Harris leads in Pennsylvania, Wisconsin, Nevada, and Michigan. When
+looking at the overall average across these states, Harris slightly
+edges out Trump, indicating her overall advantage in these swing areas.
 
-## Difference in Average Polling Percentage
-@fig-3 highlights the difference in average polling percentages by state, with positive values indicating Trump’s lead and negative values indicating Harris's.
-Trump’s lead in the three states (Arizona, Georgia, and North Carolina) is relatively narrow, with margins of less than 1 percent.
-In contrast, Harris’s lead in the states favoring her (Pennsylvania, Wisconsin, Nevada, and Michigan) ranges from 1 to 4 percent, indicating her stronger support in the states where she leads.
+\hypertarget{polling-percentage-distribution}{%
+\subsection{Polling Percentage
+Distribution}\label{polling-percentage-distribution}}
 
-```{r}
-#| label: fig-1
-#| fig-cap: "Average Polling Percentage by State"
-#| echo: false
-#| warning: false
-#| message: false
-# Calculate the average polling percentage by state for Trump and Harris
-data_avg <- data %>%
-  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
-  group_by(state, candidate_name) %>%
-  summarize(avg_pct = mean(pct, na.rm = TRUE), .groups = "drop")
+The box plot in Figure~\ref{fig-2} demonstrates the range and
+consistency of support for both candidates across each state. Trump
+shows a wider range of support, reflecting variability, while Harris has
+relatively steady polling percentages across states, maintaining higher
+consistency. Harris's support is less variable and generally centers
+around higher polling percentages compared to Trump's.
 
-# Calculate the overall average polling percentage for Trump and Harris
-overall_avg <- data %>%
-  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
-  group_by(candidate_name) %>%
-  summarize(avg_pct = mean(pct, na.rm = TRUE)) %>%
-  mutate(state = " Overall")  # Add a space before "Overall" to separate it visually
+\hypertarget{difference-in-average-polling-percentage}{%
+\subsection{Difference in Average Polling
+Percentage}\label{difference-in-average-polling-percentage}}
 
-# Combine state-level data with overall average
-combined_data <- bind_rows(data_avg, overall_avg)
+Figure~\ref{fig-3} highlights the difference in average polling
+percentages by state, with positive values indicating Trump's lead and
+negative values indicating Harris's. Trump's lead in the three states
+(Arizona, Georgia, and North Carolina) is relatively narrow, with
+margins of less than 1 percent. In contrast, Harris's lead in the states
+favoring her (Pennsylvania, Wisconsin, Nevada, and Michigan) ranges from
+1 to 4 percent, indicating her stronger support in the states where she
+leads.
 
-# Ensure "Overall" appears at the bottom with spacing
-combined_data$state <- factor(combined_data$state, levels = c(setdiff(unique(combined_data$state), " Overall"), " Overall"))
+\begin{figure}
 
-# Plot the average polling percentages by state with overall comparison
-ggplot(combined_data, aes(x = state, y = avg_pct, fill = candidate_name)) +
-  geom_bar(stat = "identity", position = position_dodge(width = 0.8), aes(color = ifelse(state == " Overall", "Overall", "State")), width = 0.6) + 
-  scale_color_manual(values = c("Overall" = "black", "State" = NA), guide = "none") +  # Add dark grey outline for "Overall" bars
-  scale_fill_manual(values = c("Donald Trump" = "#F8766D", "Kamala Harris" = "#56B4E9")) +  # Custom colors for consistency
-  labs(title = "Average Polling Percentages by State",
-       x = "State",
-       y = "Average Polling Percentage",
-       fill = "Candidate") +
-  coord_flip() +  # Flip coordinates for easier reading
-  theme_minimal() +
-  theme(
-    legend.position = "bottom",
-    axis.text.y = element_text(margin = margin(r = 10)), # Add spacing to y-axis labels
-    panel.grid.major.y = element_blank(), # Remove y-axis gridlines for clarity
-    panel.spacing = unit(1, "lines") # Increase panel spacing
-  )
+{\centering \includegraphics{paper_files/figure-pdf/fig-1-1.pdf}
 
-```
+}
 
-```{r}
-#| label: fig-2
-#| fig-cap: "Polling Percentage Distribution"
-#| echo: false
-#| warning: false
-#| message: false
-ggplot(data %>% filter(candidate_name %in% c("Donald Trump", "Kamala Harris")), 
-       aes(x = state, y = pct, fill = candidate_name)) +
-  geom_boxplot(alpha = 0.7) +
-  labs(title = "Polling Percentage Distribution by State",
-       x = "State",
-       y = "Polling Percentage",
-       fill = "Candidate") +
-  scale_fill_manual(values = c("Donald Trump" = "#F8766D", "Kamala Harris" = "#56B4E9")) +
-  theme_minimal() +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
-```
-```{r}
-#| label: fig-3
-#| fig-cap: "Difference in Average Polling Percentage"
-#| echo: false
-#| warning: false
-#| message: false
-data_diff <- data %>%
-  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
-  group_by(state) %>%
-  summarize(diff_pct = mean(pct[candidate_name == "Donald Trump"], na.rm = TRUE) - 
-                      mean(pct[candidate_name == "Kamala Harris"], na.rm = TRUE), .groups = "drop")
+\caption{\label{fig-1}Average Polling Percentage by State}
 
-ggplot(data_diff, aes(x = reorder(state, diff_pct), y = diff_pct, fill = diff_pct > 0)) +
-  geom_bar(stat = "identity", color = "darkgrey") +
-  scale_fill_manual(values = c("TRUE" = "#F8766D", "FALSE" = "#56B4E9"), 
-                    labels = c("Kamala Harris", "Donald Trump")) +
-  labs(title = "Difference in Average Polling Percentage by State",
-       x = "State",
-       y = "Difference in Polling Percentage",
-       fill = "Lead") +
-  coord_flip() +
-  theme_minimal() +
-  theme(legend.position = "bottom")
-```
+\end{figure}
 
-## Swing State Polling Prediction Model
-@fig-4 shows the trend of support rate changes for each candidate before the upcoming election, as well as the model's predicted values for the next 20 days.We predicts that Kamala Harris may win based on our model.
-```{r}
-#| label: fig-4
-#| fig-cap: "Swing State Polling Prediction Model"
-#| echo: false
-#| warning: false
-#| message: false
+\begin{figure}
 
-invisible(Sys.setlocale("LC_TIME", "en_US"))
-model_data <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
-model <- readRDS(here::here("models/model.rds"))
+{\centering \includegraphics{paper_files/figure-pdf/fig-2-1.pdf}
 
-model_data <- model_data %>%
-  mutate(predicted_pct = predict(model, newdata = ., type = "response"))
-last_date <- max(model_data$end_date, na.rm = TRUE)
-new_dates <- seq.Date(from = last_date + 1, by = "day", length.out = 20)
-new_data <- expand.grid(
-  end_date = new_dates,
-  candidate_name = unique(model_data$candidate_name)
-)
-new_data <- new_data %>%
-  mutate(
-    end_date_numeric = as.numeric(end_date), 
-  ) %>% mutate(predicted_pct = predict(model, newdata = ., type = "response"))
-all_data <- bind_rows(model_data, new_data)
+}
 
-ggplot(all_data, aes(x = end_date, y = pct, color = candidate_name)) +
-  geom_point(aes(y = average_pct/100), alpha = 0.5) + 
-  geom_line(aes(y = predicted_pct), size = 1) + 
-  labs(title = "2024 US President Polls - Predicted vs True",
-       x = "Date",
-       y = "Rate of support") +
-  theme_minimal() +
-  scale_x_date(date_labels = "%b", date_breaks = "1 month", 
-               limits = as.Date(c("2024-01-01", "2024-11-5"))) +
-  scale_y_continuous(labels = percent_format(), limits = c(0.44, 0.47))
+\caption{\label{fig-2}Polling Percentage Distribution}
 
-```
+\end{figure}
 
-# Discussion
+\begin{figure}
 
-## Impact of Key Demographics and Policy Appeals
-Harris’s lead in several swing states may be influenced by her campaign’s appeal to key demographic groups, particularly immigrants.
-The Democratic platform has emphasized social and economic benefits for immigrant communities, which may have strengthened her base in states with significant immigrant populations.
-Policies that promise support for healthcare, education, and other public services are likely contributing to Harris’s appeal among these groups, solidifying her lead in states like Nevada and Michigan.
-This demographic support provides Harris with a strategic advantage, as these communities may play a crucial role in voter turnout and loyalty.
+{\centering \includegraphics{paper_files/figure-pdf/fig-3-1.pdf}
 
-## Influence of Endorsements and High-Profile Backing
-Recently, high-profile figures like Elon Musk have publicly thrown their support behind Trump, leveraging their influence to rally support for his campaign [@Zahn2024].
-Musk’s endorsement could invigorate Trump’s base, especially among Musk’s followers and those engaged in the fields of business and technology.
-This visible backing from such influential figures has the potential to sway undecided voters and influence last-minute decisions, particularly in swing states where Trump’s lead remains narrow.
+}
 
-Musk’s endorsement might not only energize Trump’s existing supporters but could also lead to a boost in campaign funds and social media engagement, further strengthening Trump’s position.
-In closely contested states, where a few thousand votes can make a significant difference, this level of backing from a high-profile figure could be crucial.
-If Musk’s involvement draws in additional resources and amplifies Trump’s visibility, it may ultimately impact the final outcome of the election on November 5th.
+\caption{\label{fig-3}Difference in Average Polling Percentage}
 
-## Limitations of the Analysis: Focus on Swing States
-While the analysis focuses on key swing states, it does not consider the broader national picture, which includes states with clear, one-sided advantages for either candidate.
-This narrowed focus on swing states provides insights into swing areas but does not give a complete picture of the national landscape.
-Therefore, while Harris appears to have an edge in these swing states, it is unclear whether she is leading overall.
-The situation in solidly red or blue states could still shift the electoral balance, meaning Trump could potentially gain ground through strong performances in traditionally Republican states.
+\end{figure}
 
-## Potential Influence of Late Campaign Efforts
-With a few days remaining before the election, both campaigns are likely to intensify their outreach efforts, particularly in swing states.
-Trump’s recent increase in targeted advertisements and campaign rallies in swing states could energize his supporters, narrowing Harris’s lead.
-On the other hand, Harris’s campaign may focus on mobilizing key demographics, such as young and minority voters, to secure her advantage.
-Late-breaking events, public debates, or controversies could sway undecided voters and ultimately impact the election results in these states.
+\hypertarget{swing-state-polling-prediction-model}{%
+\subsection{Swing State Polling Prediction
+Model}\label{swing-state-polling-prediction-model}}
 
-## Limitations and Next Steps
-This analysis is limited to examining current polling data in swing states and does not account for unexpected shifts in voter sentiment or turnout on election day.
-Additionally, focusing exclusively on swing states omits the influence of non-swing states that may still play a role in the electoral vote tally.
-Future analyses could incorporate national polling data to provide a more comprehensive perspective and examine demographic breakdowns within each state to understand which groups are driving support for each candidate.
-Integrating data on recent campaign activities, endorsements, and voter sentiment on pressing issues could also improve the predictive accuracy of election outcomes.
+Figure~\ref{fig-4} shows the trend of support rate changes for each
+candidate before the upcoming election, as well as the model's predicted
+values for the next 20 days.We predicts that Donald Trump may win based
+on our model.
+
+\begin{figure}
+
+{\centering \includegraphics{paper_files/figure-pdf/fig-4-1.pdf}
+
+}
+
+\caption{\label{fig-4}Swing State Polling Prediction Model}
+
+\end{figure}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{impact-of-key-demographics-and-policy-appeals}{%
+\subsection{Impact of Key Demographics and Policy
+Appeals}\label{impact-of-key-demographics-and-policy-appeals}}
+
+Harris's lead in several swing states may be influenced by her
+campaign's appeal to key demographic groups, particularly immigrants.
+The Democratic platform has emphasized social and economic benefits for
+immigrant communities, which may have strengthened her base in states
+with significant immigrant populations. Policies that promise support
+for healthcare, education, and other public services are likely
+contributing to Harris's appeal among these groups, solidifying her lead
+in states like Nevada and Michigan. This demographic support provides
+Harris with a strategic advantage, as these communities may play a
+crucial role in voter turnout and loyalty.
+
+\hypertarget{influence-of-endorsements-and-high-profile-backing}{%
+\subsection{Influence of Endorsements and High-Profile
+Backing}\label{influence-of-endorsements-and-high-profile-backing}}
+
+Recently, high-profile figures like Elon Musk have publicly thrown their
+support behind Trump, leveraging their influence to rally support for
+his campaign (Zahn 2024). Musk's endorsement could invigorate Trump's
+base, especially among Musk's followers and those engaged in the fields
+of business and technology. This visible backing from such influential
+figures has the potential to sway undecided voters and influence
+last-minute decisions, particularly in swing states where Trump's lead
+remains narrow.
+
+Musk's endorsement might not only energize Trump's existing supporters
+but could also lead to a boost in campaign funds and social media
+engagement, further strengthening Trump's position. In closely contested
+states, where a few thousand votes can make a significant difference,
+this level of backing from a high-profile figure could be crucial. If
+Musk's involvement draws in additional resources and amplifies Trump's
+visibility, it may ultimately impact the final outcome of the election
+on November 5th.
+
+\hypertarget{limitations-of-the-analysis-focus-on-swing-states}{%
+\subsection{Limitations of the Analysis: Focus on Swing
+States}\label{limitations-of-the-analysis-focus-on-swing-states}}
+
+While the analysis focuses on key swing states, it does not consider the
+broader national picture, which includes states with clear, one-sided
+advantages for either candidate. This narrowed focus on swing states
+provides insights into swing areas but does not give a complete picture
+of the national landscape. Therefore, while Harris appears to have an
+edge in these swing states, it is unclear whether she is leading
+overall. The situation in solidly red or blue states could still shift
+the electoral balance, meaning Trump could potentially gain ground
+through strong performances in traditionally Republican states.
+
+\hypertarget{potential-influence-of-late-campaign-efforts}{%
+\subsection{Potential Influence of Late Campaign
+Efforts}\label{potential-influence-of-late-campaign-efforts}}
+
+With a few days remaining before the election, both campaigns are likely
+to intensify their outreach efforts, particularly in swing states.
+Trump's recent increase in targeted advertisements and campaign rallies
+in swing states could energize his supporters, narrowing Harris's lead.
+On the other hand, Harris's campaign may focus on mobilizing key
+demographics, such as young and minority voters, to secure her
+advantage. Late-breaking events, public debates, or controversies could
+sway undecided voters and ultimately impact the election results in
+these states.
+
+\hypertarget{limitations-and-next-steps}{%
+\subsection{Limitations and Next
+Steps}\label{limitations-and-next-steps}}
+
+This analysis is limited to examining current polling data in swing
+states and does not account for unexpected shifts in voter sentiment or
+turnout on election day. Additionally, focusing exclusively on swing
+states omits the influence of non-swing states that may still play a
+role in the electoral vote tally. Future analyses could incorporate
+national polling data to provide a more comprehensive perspective and
+examine demographic breakdowns within each state to understand which
+groups are driving support for each candidate. Integrating data on
+recent campaign activities, endorsements, and voter sentiment on
+pressing issues could also improve the predictive accuracy of election
+outcomes.
 
@@
 
-# Appendix A {-}
+\hypertarget{appendix-a}{%
+\section*{Appendix A}\label{appendix-a}}
+\addcontentsline{toc}{section}{Appendix A}
 
-#  Sampling Methodology Employed by New York Times and Siena College:
+\hypertarget{sampling-methodology-employed-by-new-york-times-and-siena-college}{%
+\section{Sampling Methodology Employed by New York Times and Siena
+College:}\label{sampling-methodology-employed-by-new-york-times-and-siena-college}}
 
-Our analysis and prediction utilizes data collected by a single pollster and it is important to scrutinize the sampling methodology behind the sampling methods used to determine the extent of the external validity of our predictions.
-Primarily, the data gathered by New York Times was done so with the collaboration with Sienna College through live-interviewers reaching voters by telephone.
+Our analysis and prediction utilizes data collected by a single pollster
+and it is important to scrutinize the sampling methodology behind the
+sampling methods used to determine the extent of the external validity
+of our predictions. Primarily, the data gathered by New York Times was
+done so with the collaboration with Sienna College through
+live-interviewers reaching voters by telephone.
 
-## Target Population and Sampling Frame
-The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
-Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters @nyt_poll.
-This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information.
-From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population @nyt_poll.
+\hypertarget{target-population-and-sampling-frame}{%
+\subsection{Target Population and Sampling
+Frame}\label{target-population-and-sampling-frame}}
 
-## Recruitment Methods
-The poll relies on random digit dialing to reach voters, predominantly via cell phones.
-While landlines are also called, the dominance of cellphone usage aligns with contemporary communication trends.
-This results in their rendition of random sampling, which contributes to the external validity of data.
-However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
-In fact, according to an article by Emerson College, telephone polling has become entirely obsolete @kimball_polling.
-Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling.
-Although this can be seen as random sampling, the concern of low response rates and reliance on dialing to reach voters raises concerns of selection bias.
-There are questions as to whether a certain demographic will be more responsive to being reached through a cell phone.
-Moreover, voters that are reached over the phone may feel the urge to provide more ‘socially desirable’ responses that are not reflective of their true opinions.
+The poll targets registered voters in the United States, with a
+particular focus on voters in swing states for presidential races.
+Consequently, the target population is registered voters of the United
+States of America and the sampling frame is the voter file, a national
+list of registered voters from which NYC employs random sampling to
+create their pollsters The New York Times (2024). This voter file
+contains information on more than 200 million Americans that includes
+information about their party affiliation, voting history, and basic
+demographic information. From this sampling frame, respondents are
+randomly selected while balancing key demographic and political
+characteristics through both front-end sampling and post-survey
+weighting pursuant to appropriate representation of the entire target
+population The New York Times (2024).
 
-## Non-Response Remedies
-With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics.
-The poll addresses non-response through a combination of front-end sampling adjustments (calling harder-to-reach voters) and post-survey weighting.
-Weighting is applied to ensure that the final sample aligns with the demographic and political composition of the electorate, based on voter file data.
-Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
-Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% @nyt_poll.
+\hypertarget{recruitment-methods}{%
+\subsection{Recruitment Methods}\label{recruitment-methods}}
 
-# Sampling Approach: Stratified Sampling
+The poll relies on random digit dialing to reach voters, predominantly
+via cell phones. While landlines are also called, the dominance of
+cellphone usage aligns with contemporary communication trends. This
+results in their rendition of random sampling, which contributes to the
+external validity of data. However, reaching voters by phone has become
+more difficult due to low response rates requiring many attempts to
+secure responses from certain individuals (response rates are as low as
+2\% at NYC). In fact, according to an article by Emerson College,
+telephone polling has become entirely obsolete Kimball, Mumford, and
+Taglia (2024). Despite this, the phone methodology is still seen as
+effective for its ability to quickly reach a diverse voter pool across
+various states as well as seen as the golden standard for polling.
+Although this can be seen as random sampling, the concern of low
+response rates and reliance on dialing to reach voters raises concerns
+of selection bias. There are questions as to whether a certain
+demographic will be more responsive to being reached through a cell
+phone. Moreover, voters that are reached over the phone may feel the
+urge to provide more `socially desirable' responses that are not
+reflective of their true opinions.
 
-##  Methodology
-The Times/Siena Poll employs a stratified random sampling approach to ensure that the sample accurately represents the diversity within the target population of registered voters in the United States.
-This method involves dividing the population into distinct subgroups, or “strata,” based on key characteristics such as state, age, gender, race, education level, and political affiliation.
-For example, in presidential elections, particular emphasis is placed on voters from swing states like Arizona, North Carolina, Georgia, and Pennsylvania.
-By focusing on these battleground states, the poll aims to capture the opinions of voters who are most likely to influence the election outcome.
-Once the strata are established, respondents are randomly selected within each group, ensuring that all demographic groups are appropriately represented in proportion to their actual distribution within the electorate.
-Furthermore, post-survey weighting is employed to more closely resemble this distribution.
+\hypertarget{non-response-remedies}{%
+\subsection{Non-Response Remedies}\label{non-response-remedies}}
 
-## Advantages
-Stratified sampling offers the advantage of higher precision in representing the population's diversity, as each subgroup is proportionally represented.
-By breaking down the sample into distinct groups, the Times/Siena Poll can adjust for demographic variations between states or voter groups, which is particularly useful in a diverse electorate.
-This approach helps to minimize sampling error by ensuring that all significant voter subgroups are included, thus increasing the reliability of the poll’s predictions.
-It is standard practice for them to sample 1,000 respondents for their polls.
-Using stratified sampling to have this sample size closely resemble that of the entire target population cuts costs and provides efficient real-time data.
+With a response rate of 2\%, there is valid concern over non-response
+bias underrepresenting certain demographics. The poll addresses
+non-response through a combination of front-end sampling adjustments
+(calling harder-to-reach voters) and post-survey weighting. Weighting is
+applied to ensure that the final sample aligns with the demographic and
+political composition of the electorate, based on voter file data.
+Non-response bias is a persistent challenge, and even though weighting
+helps, it's impossible to be certain that respondents are fully
+representative of those who do not respond. Experiments with alternative
+methods, such as mail surveys with incentives of cash vouchers have
+shown to increase response rate up to 30\% The New York Times (2024).
 
-## Stratified Sampling over Random Sampling
+\hypertarget{sampling-approach-stratified-sampling}{%
+\section{Sampling Approach: Stratified
+Sampling}\label{sampling-approach-stratified-sampling}}
 
-If the methodology randomly sampled from the target population without regard for the distribution of demographics in the state, significant increases to the sample sizes have to be made.
-Random sampling will have largely less precision in representing the distribution of different demographics within a given state unless a large enough sample size were to be drawn.
-Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources.
-With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is @tellingstories.
-As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.
+\hypertarget{methodology}{%
+\subsection{Methodology}\label{methodology}}
 
-## Challenges and Trade-offs
+The Times/Siena Poll employs a stratified random sampling approach to
+ensure that the sample accurately represents the diversity within the
+target population of registered voters in the United States. This method
+involves dividing the population into distinct subgroups, or ``strata,''
+based on key characteristics such as state, age, gender, race, education
+level, and political affiliation. For example, in presidential
+elections, particular emphasis is placed on voters from swing states
+like Arizona, North Carolina, Georgia, and Pennsylvania. By focusing on
+these battleground states, the poll aims to capture the opinions of
+voters who are most likely to influence the election outcome. Once the
+strata are established, respondents are randomly selected within each
+group, ensuring that all demographic groups are appropriately
+represented in proportion to their actual distribution within the
+electorate. Furthermore, post-survey weighting is employed to more
+closely resemble this distribution.
 
-Although stratified sampling improves representativeness, it presents certain challenges in execution.
-First, identifying and reaching a sufficient number of respondents from harder-to-reach groups (such as young voters, minority populations, and those without reliable phone access) can be difficult, especially given the 2% response rate.
-To counterbalance the low response rates, the poll requires multiple call attempts and careful post-survey weighting to adjust for any potential underrepresentation.
-Additionally, while phone polling offers broad geographic reach and a standardized mode of data collection, it limits the sample to voters with phone access who are willing to participate in phone interviews, potentially introducing selection bias if certain demographics are less reachable by phone.
-Although New York Times/Sienna College employs random digit dialing from their sampling frame, their rendition of sample recruitment requires them to sample individuals according to quotas, resulting in nonprobability sampling.
+\hypertarget{advantages}{%
+\subsection{Advantages}\label{advantages}}
 
-## Evaluation of Questionnaire Design in the Times/Siena Poll
+Stratified sampling offers the advantage of higher precision in
+representing the population's diversity, as each subgroup is
+proportionally represented. By breaking down the sample into distinct
+groups, the Times/Siena Poll can adjust for demographic variations
+between states or voter groups, which is particularly useful in a
+diverse electorate. This approach helps to minimize sampling error by
+ensuring that all significant voter subgroups are included, thus
+increasing the reliability of the poll's predictions. It is standard
+practice for them to sample 1,000 respondents for their polls. Using
+stratified sampling to have this sample size closely resemble that of
+the entire target population cuts costs and provides efficient real-time
+data.
 
-### Strengths
+\hypertarget{stratified-sampling-over-random-sampling}{%
+\subsection{Stratified Sampling over Random
+Sampling}\label{stratified-sampling-over-random-sampling}}
 
-The Times/Siena Poll’s approach to questionnaire design reflects a careful effort to craft unbiased, relevant, and inclusive questions.
-By tailoring questions to current events and topics of widespread interest, the poll aims to capture public sentiment on issues that directly affect voters' attitudes, such as economic conditions or recent political debates.
-This responsiveness to current events strengthens the poll's relevance and allows it to track shifts in opinion over time.
-The poll’s commitment to neutrality is a significant strength.
-Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented.
-The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups @nyt_poll.
-Clarity is also a central focus in their questionnaire development.
-The team emphasizes ensuring that each question is clear and unambiguous, minimizing the risk of misinterpretation.
-This dedication to straightforward, widely understandable questions improves the validity of responses, as it reduces the chance that respondents interpret questions differently based on background or knowledge level.
+If the methodology randomly sampled from the target population without
+regard for the distribution of demographics in the state, significant
+increases to the sample sizes have to be made. Random sampling will have
+largely less precision in representing the distribution of different
+demographics within a given state unless a large enough sample size were
+to be drawn. Although it is ideal to have probability based sampling
+increasingly resemble the demographic distribution quota with growing
+sample sizes, it is unfeasible to conduct such a large scale poll as
+this approach would encounter a limitation of resources. With declining
+response rates and the difficulty of reaching voters, New York
+Times/Siena's nonprobability sampling is a more realistic and efficient
+method of polling than probability sampling is
+(\textbf{tellingstories?}). As such, the stratified sampling approach
+allows New York Times/Siena to represent the entire target population
+with a sample size of 1,000.
 
-### Limitations
+\hypertarget{challenges-and-trade-offs}{%
+\subsection{Challenges and Trade-offs}\label{challenges-and-trade-offs}}
 
-Despite the strengths of the Times/Siena Poll’s questionnaire design, there are some limitations.
-One notable concern is that, although the poll tries to avoid leading questions, any standardized questionnaire may still unintentionally prime respondents or introduce subtle biases, especially when questions involve sensitive or polarizing topics.
-Although the pollster tries to avoid attrition bias by keeping each interview less than 15 minutes, in seeking to make questions clear and concise, the questionnaire may not capture the full nuance of voter opinions, especially on multifaceted issues like economic policy or social justice.
-While the poll strives to capture real views without introducing new ideas, respondents are still prone to a social desirability bias.
-This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions.
-Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses @psychology_survey_response.
+Although stratified sampling improves representativeness, it presents
+certain challenges in execution. First, identifying and reaching a
+sufficient number of respondents from harder-to-reach groups (such as
+young voters, minority populations, and those without reliable phone
+access) can be difficult, especially given the 2\% response rate. To
+counterbalance the low response rates, the poll requires multiple call
+attempts and careful post-survey weighting to adjust for any potential
+underrepresentation. Additionally, while phone polling offers broad
+geographic reach and a standardized mode of data collection, it limits
+the sample to voters with phone access who are willing to participate in
+phone interviews, potentially introducing selection bias if certain
+demographics are less reachable by phone. Although New York Times/Sienna
+College employs random digit dialing from their sampling frame, their
+rendition of sample recruitment requires them to sample individuals
+according to quotas, resulting in nonprobability sampling.
+
+\hypertarget{evaluation-of-questionnaire-design-in-the-timessiena-poll}{%
+\subsection{Evaluation of Questionnaire Design in the Times/Siena
+Poll}\label{evaluation-of-questionnaire-design-in-the-timessiena-poll}}
+
+\hypertarget{strengths}{%
+\subsubsection{Strengths}\label{strengths}}
+
+The Times/Siena Poll's approach to questionnaire design reflects a
+careful effort to craft unbiased, relevant, and inclusive questions. By
+tailoring questions to current events and topics of widespread interest,
+the poll aims to capture public sentiment on issues that directly affect
+voters' attitudes, such as economic conditions or recent political
+debates. This responsiveness to current events strengthens the poll's
+relevance and allows it to track shifts in opinion over time. The poll's
+commitment to neutrality is a significant strength. Each question is
+designed to ensure that respondents, regardless of their political
+views, feel that their perspectives are fairly represented. The team
+behind the poll spends substantial time crafting response options to
+reflect a balanced spectrum of views, minimizing potential response bias
+and enhancing the questionnaire's reliability across different
+demographic and ideological groups The New York Times (2024). Clarity is
+also a central focus in their questionnaire development. The team
+emphasizes ensuring that each question is clear and unambiguous,
+minimizing the risk of misinterpretation. This dedication to
+straightforward, widely understandable questions improves the validity
+of responses, as it reduces the chance that respondents interpret
+questions differently based on background or knowledge level.
+
+\hypertarget{limitations}{%
+\subsubsection{Limitations}\label{limitations}}
+
+Despite the strengths of the Times/Siena Poll's questionnaire design,
+there are some limitations. One notable concern is that, although the
+poll tries to avoid leading questions, any standardized questionnaire
+may still unintentionally prime respondents or introduce subtle biases,
+especially when questions involve sensitive or polarizing topics.
+Although the pollster tries to avoid attrition bias by keeping each
+interview less than 15 minutes, in seeking to make questions clear and
+concise, the questionnaire may not capture the full nuance of voter
+opinions, especially on multifaceted issues like economic policy or
+social justice. While the poll strives to capture real views without
+introducing new ideas, respondents are still prone to a social
+desirability bias. This is especially possible in phone interviews,
+where respondents may be more inclined to provide answers they perceive
+as socially acceptable rather than expressing their true opinions.
+Although the design aims to be fair, the influence of an interviewer's
+presence may subtly affect responses Roger Tourangeau and Rasinski
+(2000).
 
@@
 
-# Appendix B {-}
+\hypertarget{appendix-b}{%
+\section*{Appendix B}\label{appendix-b}}
+\addcontentsline{toc}{section}{Appendix B}
 
-Pursuant to accurately predicting the winner of the presidential election with the electoral college system, there are assumptions that need to be assessed.
-The United States of America’s electoral college system creates a special environment where votes in some states are disproportionately more influential than that of others and candidates are not elected based on popular vote, but on the majority of electoral votes they get.
+Pursuant to accurately predicting the winner of the presidential
+election with the electoral college system, there are assumptions that
+need to be assessed. The United States of America's electoral college
+system creates a special environment where votes in some states are
+disproportionately more influential than that of others and candidates
+are not elected based on popular vote, but on the majority of electoral
+votes they get.
 
-## Assumption 1:
+\hypertarget{assumption-1}{%
+\subsection{Assumption 1:}\label{assumption-1}}
 
-Nation-level Popular Vote is irrelevant in our methodology since president electors are chosen based on electoral votes.
+Nation-level Popular Vote is irrelevant in our methodology since
+president electors are chosen based on electoral votes.
 
-##  Assumption 2:
+\hypertarget{assumption-2}{%
+\subsection{Assumption 2:}\label{assumption-2}}
 
-Based on historical and polling data, some states’ electoral votes are predetermined as either Democrat or Republican.
-Therefore, it is more prudent to shift focus over to swing states where outcomes are uncertain.
-This assumption is accompanied with the challenge of determining what states qualify as “swing states”.
-However, on this issue, there is consensus on which states qualify as swing states.
-Pollsters such as  New York Times have their metric for determining which  states are 'battleground states'.
-As of 2024, our methodology should direct all our resources to acquiring voting data on the following states (New York Times).
-This assumption results in each presidential candidate starting off with a set number of electoral votes.
+Based on historical and polling data, some states' electoral votes are
+predetermined as either Democrat or Republican. Therefore, it is more
+prudent to shift focus over to swing states where outcomes are
+uncertain. This assumption is accompanied with the challenge of
+determining what states qualify as ``swing states''. However, on this
+issue, there is consensus on which states qualify as swing states.
+Pollsters such as New York Times have their metric for determining which
+states are `battleground states'. As of 2024, our methodology should
+direct all our resources to acquiring voting data on the following
+states (New York Times). This assumption results in each presidential
+candidate starting off with a set number of electoral votes.
 
-##  Swing States
+\hypertarget{swing-states}{%
+\subsection{Swing States}\label{swing-states}}
 
-According to 2024 polling data conducted by New York Times, the swing states are determined to be the following @boyce_swing_states:
+According to 2024 polling data conducted by New York Times, the swing
+states are determined to be the following Boyce et al. (2024):
 
-Pennsylvania
-Georgia
-North Carolina
-Michigan
-Arizona
-Wisconsin
-Nevada
+Pennsylvania Georgia North Carolina Michigan Arizona Wisconsin Nevada
 
-## Feasibility of Reaching Voters: Justification of Online Panels
+\hypertarget{feasibility-of-reaching-voters-justification-of-online-panels}{%
+\subsection{Feasibility of Reaching Voters: Justification of Online
+Panels}\label{feasibility-of-reaching-voters-justification-of-online-panels}}
 
-According to the New York Times, with a sample of 1000 individual votes, there is a margin of error of around three to four percentages.
-With $100,000, there are limitations on the labor and resources that is required to poll 1000 voters while balancing out demographics through dialing.
-Furthermore, there is additional filtering of our sample frame to determine likely voters.
-Assuming New York Times’ 2% voter response rate, to sample 1000 voters, at least 50,000 voters will need to be called.
-It is likely that our team will be dialing abundantly more than 50,000 times since it is an unreasonable assumption that every voter we call would pick up or be available to provide a response.
-There is also the fact that our team does not carry the same credibility and history of acquiring poll data as the New York Times does, resulting in more reluctance for voters to share information with us.
-Therefore, it is not feasible for our methodology to employ telephone dialing as our method to reach voters.
-Instead, we focus on online panels and surveys with incentives for completing the survey correctly.
-However, online panels and surveys come with their own set of challenges and weaknesses that must be addressed in our methodology.
-Primarily, the problem of self-selection in online panels disrupts the random selection that allows the external validity of our predictions.
-Moreover, there is apossibility that we acquire responses from respondents that are not likely to vote, gaining data from outside our target population.
-Even if we distribute the panels randomly among swing states, responses are still corrupted by selection bias that occurs from responses that are provided from demographics that feel more passionately about the election or are more likely to respond to online panels.
-Unlike telephone dialing, we have less control over the specific demographic we want to target, resulting in a less stratified data that is representative of the target population overall.
+According to the New York Times, with a sample of 1000 individual votes,
+there is a margin of error of around three to four percentages. With
+\$100,000, there are limitations on the labor and resources that is
+required to poll 1000 voters while balancing out demographics through
+dialing. Furthermore, there is additional filtering of our sample frame
+to determine likely voters. Assuming New York Times' 2\% voter response
+rate, to sample 1000 voters, at least 50,000 voters will need to be
+called. It is likely that our team will be dialing abundantly more than
+50,000 times since it is an unreasonable assumption that every voter we
+call would pick up or be available to provide a response. There is also
+the fact that our team does not carry the same credibility and history
+of acquiring poll data as the New York Times does, resulting in more
+reluctance for voters to share information with us. Therefore, it is not
+feasible for our methodology to employ telephone dialing as our method
+to reach voters. Instead, we focus on online panels and surveys with
+incentives for completing the survey correctly. However, online panels
+and surveys come with their own set of challenges and weaknesses that
+must be addressed in our methodology. Primarily, the problem of
+self-selection in online panels disrupts the random selection that
+allows the external validity of our predictions. Moreover, there is
+apossibility that we acquire responses from respondents that are not
+likely to vote, gaining data from outside our target population. Even if
+we distribute the panels randomly among swing states, responses are
+still corrupted by selection bias that occurs from responses that are
+provided from demographics that feel more passionately about the
+election or are more likely to respond to online panels. Unlike
+telephone dialing, we have less control over the specific demographic we
+want to target, resulting in a less stratified data that is
+representative of the target population overall.
 
-##	Remedies for Online Panels
+\hypertarget{remedies-for-online-panels}{%
+\subsection{Remedies for Online
+Panels}\label{remedies-for-online-panels}}
 
-### Weighting Adjustments
+\hypertarget{weighting-adjustments}{%
+\subsubsection{Weighting Adjustments}\label{weighting-adjustments}}
 
-Although online panels offer an imperfect solution to the limited resources our team will work with, there are remedies that can address underrepresentation brought by selection bias.
-As NYC and Siena College does, post-survey weighting can help us represent our target population more accurately.
-This is an effective way to adjust our sample based on demographic data and historical turnout patterns within each state.
-By weighting responses to mirror actual voter demographics from a particular state, the survey results can approximate a more realistic projection of the electorate.
-These weighting adjustments help to maintain the integrity of our sample, closely resembling the target population of a state.
+Although online panels offer an imperfect solution to the limited
+resources our team will work with, there are remedies that can address
+underrepresentation brought by selection bias. As NYC and Siena College
+does, post-survey weighting can help us represent our target population
+more accurately. This is an effective way to adjust our sample based on
+demographic data and historical turnout patterns within each state. By
+weighting responses to mirror actual voter demographics from a
+particular state, the survey results can approximate a more realistic
+projection of the electorate. These weighting adjustments help to
+maintain the integrity of our sample, closely resembling the target
+population of a state.
 
-### Screening for Likely Voters
+\hypertarget{screening-for-likely-voters}{%
+\subsubsection{Screening for Likely
+Voters}\label{screening-for-likely-voters}}
 
-Although weighting adjustments helpsus represent our target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels since it will be advertised online.
-To produce accurate predictions of election results, our sample needs to be acquired from a target population that will participate in the election.
-Therefore, it becomes necessary to include screening questions designed to filter for likely voters, based on voting history or engagement levels.
-Our survey includes questions that pertain to voting history, interest and engagement, voting intention, and eligibility.
-Responses to these questions will be used to produce an aggregate “likely voter” score that filters for the target population enabling for more accurate predictions of the presidential election.
+Although weighting adjustments helpsus represent our target population
+more closely, there is nothing to stop respondents from outside our
+target population to participate in our panels since it will be
+advertised online. To produce accurate predictions of election results,
+our sample needs to be acquired from a target population that will
+participate in the election. Therefore, it becomes necessary to include
+screening questions designed to filter for likely voters, based on
+voting history or engagement levels. Our survey includes questions that
+pertain to voting history, interest and engagement, voting intention,
+and eligibility. Responses to these questions will be used to produce an
+aggregate ``likely voter'' score that filters for the target population
+enabling for more accurate predictions of the presidential election.
 
-##  Elements of Our Survey
-To gather accurate responses from a diverse and representative set of likely voters, our survey design carefully adheres to best practices in methodology.
-Given our goal to avoid attrition bias, we’ve restricted the estimated survey completion time to under ten minutes.
-This constraint is stricter than the fifteen-minute benchmark typically used by NYC and Siena College for telephone surveys, as online surveys require shorter durations to maintain respondent engagement.
-Our survey is divided into three main sections: Preamble, Eligibility, and Party Affiliation.
+\hypertarget{elements-of-our-survey}{%
+\subsection{Elements of Our Survey}\label{elements-of-our-survey}}
 
-### Preamble
-The Preamble serves as an introductory section that aims to establish transparency and motivate respondents to complete the survey accurately.
-This introduction begins with an explanation of the lottery-style incentive offered for survey completion.
-Rather than small individual payments, participants have a chance to win a larger prize if they complete the survey, a choice that aligns with budget constraints while enhancing participation rates.
-To encourage honest responses, respondents are assured of the anonymity of their answers, as well as the fact that their responses will be used solely for research purposes.
-This transparency fosters trust and can reduce hesitation when sharing political preferences.
-Information about the survey’s purpose is provided sparingly to minimize any potential response bias, as we communicate that the survey concerns voting and political engagement while omitting specific details that could influence responses, such as particular issues or candidate names.
-Additionally, respondents have the option to input a referral code if invited by a friend or family member, which can increase their chances of winning the lottery and encourage participation through word-of-mouth.
-We also request information on the relationship with the referrer to monitor potential demographic clustering in cases where social or familial ties might influence responses.
+To gather accurate responses from a diverse and representative set of
+likely voters, our survey design carefully adheres to best practices in
+methodology. Given our goal to avoid attrition bias, we've restricted
+the estimated survey completion time to under ten minutes. This
+constraint is stricter than the fifteen-minute benchmark typically used
+by NYC and Siena College for telephone surveys, as online surveys
+require shorter durations to maintain respondent engagement. Our survey
+is divided into three main sections: Preamble, Eligibility, and Party
+Affiliation.
 
-### Eligibility
-The Eligibility section focuses on ensuring that respondents meet the criteria necessary for inclusion in our target population, specifically targeting likely voters within designated swing states to improve the relevance and accuracy of our sample for election predictions.
-This section begins by asking for respondents' state of residence, age, race, and other preliminary demographic information.
-To further narrow our sample to those most likely to vote, we employ several screening questions related to voting history, political engagement, and voting intentions.
-These questions help exclude individuals who are unlikely to participate in the election, thus refining our sample to reflect the likely voting population.
+\hypertarget{preamble}{%
+\subsubsection{Preamble}\label{preamble}}
 
-###  Party Affiliation
-Party Affiliation addresses respondents’ political leanings and past voting behavior.
-This section explores their current preference for presidential candidates and parties and asks how they voted in previous elections.
-By differentiating between party and candidate preference, we can identify any variance in their voting behavior and assess whether respondents’ decisions align more strongly with party or individual candidate considerations.
-This section also explores whether respondents are informed about their choices, asking questions to determine whether they are aware of both candidates or have researched their policies.
-By gathering these insights, we can create a profile of the respondent’s political orientation, which allows for a nuanced interpretation of voting intentions that goes beyond simple party preference.
+The Preamble serves as an introductory section that aims to establish
+transparency and motivate respondents to complete the survey accurately.
+This introduction begins with an explanation of the lottery-style
+incentive offered for survey completion. Rather than small individual
+payments, participants have a chance to win a larger prize if they
+complete the survey, a choice that aligns with budget constraints while
+enhancing participation rates. To encourage honest responses,
+respondents are assured of the anonymity of their answers, as well as
+the fact that their responses will be used solely for research purposes.
+This transparency fosters trust and can reduce hesitation when sharing
+political preferences. Information about the survey's purpose is
+provided sparingly to minimize any potential response bias, as we
+communicate that the survey concerns voting and political engagement
+while omitting specific details that could influence responses, such as
+particular issues or candidate names. Additionally, respondents have the
+option to input a referral code if invited by a friend or family member,
+which can increase their chances of winning the lottery and encourage
+participation through word-of-mouth. We also request information on the
+relationship with the referrer to monitor potential demographic
+clustering in cases where social or familial ties might influence
+responses.
 
-##  Distribution of Online Panels
-The online panel method provides valuable flexibility in how surveys are distributed, enabling targeted outreach in regions crucial to our election prediction model.
-Since the distribution strategy will absorb a significant portion of the budget, this section outlines our plan for cost-effective, targeted, and controlled distribution, aimed at achieving a sample that represents voters in key swing states while addressing biases inherent to online panel surveys.
+\hypertarget{eligibility}{%
+\subsubsection{Eligibility}\label{eligibility}}
 
-###   Swing State Representation
-To capture a meaningful sample for predicting election results, we target respondents exclusively from key swing states where voting outcomes remain uncertain.
-By focusing our resources on swing states, we enhance the relevance of our sample to the Electoral College system, which relies heavily on swing state outcomes.
-Achieving this requires not only careful selection of digital platforms but also strategic advertising in locally relevant spaces.
-The lottery-style incentive, with a $5,000 voucher offered to one lucky respondent, serves as an appealing motivator designed to increase participation.
-We will advertise the survey on websites, forums, and marketplaces that have high traffic within our target states.
-Examples include social media channels, local news sites, and state-specific online communities.
-Additionally, we may utilize geo-targeted ads on platforms like Google and Facebook to directly reach residents of these swing states, optimizing our budget by focusing on the digital spaces our target demographic frequents.
-A significant portion of the budget will thus be allocated to these state-specific online advertisements, which not only promote the survey but also help ensure that respondents fit our target profile.
+The Eligibility section focuses on ensuring that respondents meet the
+criteria necessary for inclusion in our target population, specifically
+targeting likely voters within designated swing states to improve the
+relevance and accuracy of our sample for election predictions. This
+section begins by asking for respondents' state of residence, age, race,
+and other preliminary demographic information. To further narrow our
+sample to those most likely to vote, we employ several screening
+questions related to voting history, political engagement, and voting
+intentions. These questions help exclude individuals who are unlikely to
+participate in the election, thus refining our sample to reflect the
+likely voting population.
 
-###   Referral Mechanics
-To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey.
-Each referral allows the original respondent to gain an additional entry in the lottery, increasing their chances of winning.
-This referral incentive taps into snowball sampling, where respondents refer people within their network to participate, expanding our pool of respondents organically.
-However, using snowball sampling in an election survey introduces potential biases, particularly the risk of overrepresentation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies.
-To mitigate this, we will place specific restrictions on the referral program.
-Each respondent will be limited to referring only one other individual, minimizing the potential for overly clustered referrals.
-Additionally, we will require respondents to identify their relationship with each referral, helping us monitor homogeneity in our responses.
-By balancing the benefits of snowball sampling with these restrictions, we aim to expand the reach of our survey into difficult to reach demographics without compromising the representativeness of the sample.
+\hypertarget{party-affiliation}{%
+\subsubsection{Party Affiliation}\label{party-affiliation}}
 
-# Budget Allocation
-  Advertisements for sampling recruitment: $70,000
-  Prize Pool for Incentive: $5,000
-  Data Processing and Cleaning: $15,000
-  Miscellaneous Expenses: $5,000
-  Petty Cash: $5,000
+Party Affiliation addresses respondents' political leanings and past
+voting behavior. This section explores their current preference for
+presidential candidates and parties and asks how they voted in previous
+elections. By differentiating between party and candidate preference, we
+can identify any variance in their voting behavior and assess whether
+respondents' decisions align more strongly with party or individual
+candidate considerations. This section also explores whether respondents
+are informed about their choices, asking questions to determine whether
+they are aware of both candidates or have researched their policies. By
+gathering these insights, we can create a profile of the respondent's
+political orientation, which allows for a nuanced interpretation of
+voting intentions that goes beyond simple party preference.
 
-#  Idealized Questionnaire and Survey
+\hypertarget{distribution-of-online-panels}{%
+\subsection{Distribution of Online
+Panels}\label{distribution-of-online-panels}}
 
-https://docs.google.com/forms/d/117wC8f1rBW_bd5glEdiR-7823-02A3HiD5EzQuT1GVw/edit
+The online panel method provides valuable flexibility in how surveys are
+distributed, enabling targeted outreach in regions crucial to our
+election prediction model. Since the distribution strategy will absorb a
+significant portion of the budget, this section outlines our plan for
+cost-effective, targeted, and controlled distribution, aimed at
+achieving a sample that represents voters in key swing states while
+addressing biases inherent to online panel surveys.
 
-# Structure
+\hypertarget{swing-state-representation}{%
+\subsubsection{Swing State
+Representation}\label{swing-state-representation}}
 
-## Preamble
+To capture a meaningful sample for predicting election results, we
+target respondents exclusively from key swing states where voting
+outcomes remain uncertain. By focusing our resources on swing states, we
+enhance the relevance of our sample to the Electoral College system,
+which relies heavily on swing state outcomes. Achieving this requires
+not only careful selection of digital platforms but also strategic
+advertising in locally relevant spaces. The lottery-style incentive,
+with a \$5,000 voucher offered to one lucky respondent, serves as an
+appealing motivator designed to increase participation. We will
+advertise the survey on websites, forums, and marketplaces that have
+high traffic within our target states. Examples include social media
+channels, local news sites, and state-specific online communities.
+Additionally, we may utilize geo-targeted ads on platforms like Google
+and Facebook to directly reach residents of these swing states,
+optimizing our budget by focusing on the digital spaces our target
+demographic frequents. A significant portion of the budget will thus be
+allocated to these state-specific online advertisements, which not only
+promote the survey but also help ensure that respondents fit our target
+profile.
+
+\hypertarget{referral-mechanics}{%
+\subsubsection{Referral Mechanics}\label{referral-mechanics}}
+
+To further broaden our reach without exponentially increasing
+advertising costs, we incorporate a referral system that rewards
+respondents for inviting others to complete the survey. Each referral
+allows the original respondent to gain an additional entry in the
+lottery, increasing their chances of winning. This referral incentive
+taps into snowball sampling, where respondents refer people within their
+network to participate, expanding our pool of respondents organically.
+However, using snowball sampling in an election survey introduces
+potential biases, particularly the risk of overrepresentation of
+individuals with similar political views, as respondents are likely to
+refer to close contacts who may share similar ideologies. To mitigate
+this, we will place specific restrictions on the referral program. Each
+respondent will be limited to referring only one other individual,
+minimizing the potential for overly clustered referrals. Additionally,
+we will require respondents to identify their relationship with each
+referral, helping us monitor homogeneity in our responses. By balancing
+the benefits of snowball sampling with these restrictions, we aim to
+expand the reach of our survey into difficult to reach demographics
+without compromising the representativeness of the sample.
+
+\hypertarget{budget-allocation}{%
+\section{Budget Allocation}\label{budget-allocation}}
+
+Advertisements for sampling recruitment: \$70,000 Prize Pool for
+Incentive: \$5,000 Data Processing and Cleaning: \$15,000 Miscellaneous
+Expenses: \$5,000 Petty Cash: \$5,000
+
+\hypertarget{idealized-questionnaire-and-survey}{%
+\section{Idealized Questionnaire and
+Survey}\label{idealized-questionnaire-and-survey}}
+
+https://docs.google.com/forms/d/117wC8f1rBW\_bd5glEdiR-7823-02A3HiD5EzQuT1GVw/edit
+
+\hypertarget{structure}{%
+\section{Structure}\label{structure}}
+
+\hypertarget{preamble-1}{%
+\subsection{Preamble}\label{preamble-1}}
 
@@
 
-Introduction: Thank you for your participation in our $5,000 giveaway program.
+Introduction: Thank you for your participation in our \$5,000 giveaway
+program.
 
-For entry, please complete the survey in its entirety below.
-Please be informed that your answers are strictly confidential and will, under no circumstances, be shared with any party, group, or persons of affiliation.
+For entry, please complete the survey in its entirety below. Please be
+informed that your answers are strictly confidential and will, under no
+circumstances, be shared with any party, group, or persons of
+affiliation.
 
-$5,000 Cash Voucher Program Details: Completing the survey below qualifies as one entry into our giveaway.
-Each participant receives a unique entry identifier, and every entry will have an equal chance in our final random selection of the prize winner.
-Please note that each individual may complete only one survey.
+\$5,000 Cash Voucher Program Details: Completing the survey below
+qualifies as one entry into our giveaway. Each participant receives a
+unique entry identifier, and every entry will have an equal chance in
+our final random selection of the prize winner. Please note that each
+individual may complete only one survey.
 
-Referral Program: Our referral program offers you the chance to increase your odds of winning.
-After completing the survey, you’ll receive a unique referral code.
-If a friend or associate completes the survey using your code, your total number of entries doubles, effectively doubling your chances of winning the $5,000 prize.
+Referral Program: Our referral program offers you the chance to increase
+your odds of winning. After completing the survey, you'll receive a
+unique referral code. If a friend or associate completes the survey
+using your code, your total number of entries doubles, effectively
+doubling your chances of winning the \$5,000 prize.
 
-Finally, we wish to clarify that this survey is conducted purely for research purposes and is entirely unaffiliated with any political party, organization, or individual in a position of power.
-Our goal is to gain insight into the evolving political landscape and levels of public engagement.
+Finally, we wish to clarify that this survey is conducted purely for
+research purposes and is entirely unaffiliated with any political party,
+organization, or individual in a position of power. Our goal is to gain
+insight into the evolving political landscape and levels of public
+engagement.
 
@@
 
-If you have entered a referral code above, please indicate the relationship with the referee from the best choice below.
-Friend
-Associate
-Relative
-Other…
+If you have entered a referral code above, please indicate the
+relationship with the referee from the best choice below. Friend
+Associate Relative Other\ldots{}
 
-## Eligibility
-Do you meet your state's residency requirements?
-Yes
-No (End Survey)
-Please select "N/A" from the options below if you reside in North Dakota. 
-Which of the following best describes you?
-I am registered to vote
-I am not registered to vote
-I plan to register
-N/A
-Full Name (For identification of $5,000 cash winner)
-From which state will you be vote for the next president of the United States of America?
-Where can we reach you when we announce the winner?
-E-mail
-Telephone
-Other…
-Contact information
-**We will not use this for any other purpose than to announce winners. It will only be used to reach our lucky winner for instructions on receiving the cash prize.
-Which of the following age groups best describes you?
-18-25
-26-31
-32-40
-41-50
-51-60
-61-80
-81-125
-Under 18
-Which of the following best describes you?
-American Indian or Alaskan Native
-Asian
-African American
-Hispanic or Latino
-Native Hawaiian or Pacific Islander
-White
-Middle Eastern or North African
-Other…
-What is your gender?
-Male
-Female
-Prefer not to say
-Other…
-Which of the following situations best describe you?
-I did not vote in the 2020 presidential election
-I planned to vote but wasn’t able to
-I voted in the 2020 presidential election
-How likely are you to vote in the upcoming election?
-Very unlikely
-1
-2
-3
-Very likely
-Have you attended a presidential rally or their campaigns this year?
-Yes
-No
-Only in the past
+\hypertarget{eligibility-1}{%
+\subsection{Eligibility}\label{eligibility-1}}
+
+Do you meet your state's residency requirements? Yes No (End Survey)
+Please select ``N/A'' from the options below if you reside in North
+Dakota. Which of the following best describes you? I am registered to
+vote I am not registered to vote I plan to register N/A Full Name (For
+identification of \$5,000 cash winner) From which state will you be vote
+for the next president of the United States of America? Where can we
+reach you when we announce the winner? E-mail Telephone Other\ldots{}
+Contact information **We will not use this for any other purpose than to
+announce winners. It will only be used to reach our lucky winner for
+instructions on receiving the cash prize. Which of the following age
+groups best describes you? 18-25 26-31 32-40 41-50 51-60 61-80 81-125
+Under 18 Which of the following best describes you? American Indian or
+Alaskan Native Asian African American Hispanic or Latino Native Hawaiian
+or Pacific Islander White Middle Eastern or North African Other\ldots{}
+What is your gender? Male Female Prefer not to say Other\ldots{} Which
+of the following situations best describe you? I did not vote in the
+2020 presidential election I planned to vote but wasn't able to I voted
+in the 2020 presidential election How likely are you to vote in the
+upcoming election? Very unlikely 1 2 3 Very likely Have you attended a
+presidential rally or their campaigns this year? Yes No Only in the past
 On a scale of 1 to 3, how closely do you follow the presidential race?
-Not at all
-1
-2
-3
-4
-5
-Very closely
+Not at all 1 2 3 4 5 Very closely
 
-## Party Affiliation
-Which party do you prefer a candidate to be chosen from?
-Democratic Party's candidate
-Republican Party's candidate
-Another Party's candidate
-In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
-Donald Trump
-Joe Biden
-Neither
-Other…
-If planning to vote, which presidential candidate are you planning to vote for?
-If you are abstaining, please select which candidate you feel more strongly about.
-Donald Trump
-Kamala Harris
-Other...
+\hypertarget{party-affiliation-1}{%
+\subsection{Party Affiliation}\label{party-affiliation-1}}
+
+Which party do you prefer a candidate to be chosen from? Democratic
+Party's candidate Republican Party's candidate Another Party's candidate
+In the 2020 presidential election, who did you vote for? If you did not
+vote, who would you have voted for? Donald Trump Joe Biden Neither
+Other\ldots{} If planning to vote, which presidential candidate are you
+planning to vote for? If you are abstaining, please select which
+candidate you feel more strongly about. Donald Trump Kamala Harris
+Other\ldots{}
 
@@
 
-# Additional data details
+\hypertarget{additional-data-details}{%
+\section{Additional data details}\label{additional-data-details}}
 
@@
 
-# Model details {#sec-model-details}
+\hypertarget{sec-model-details}{%
+\section{Model details}\label{sec-model-details}}
 
-## Posterior predictive check
+\hypertarget{posterior-predictive-check}{%
+\subsection{Posterior predictive
+check}\label{posterior-predictive-check}}
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
-This shows that the posterior predictive density closely follows the observed data density.
-Discrepancies between the two suggest that the model may be missing some aspect of the data structure or variability, which could guide potential model adjustments or refinement.
+In Figure~\ref{fig-ppcheckandposteriorvsprior-1} we implement a
+posterior predictive check. This shows that the posterior predictive
+density closely follows the observed data density. Discrepancies between
+the two suggest that the model may be missing some aspect of the data
+structure or variability, which could guide potential model adjustments
+or refinement.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
-This shows the prior for each parameter is centered around zero, but the posterior shows more precise estimates for each candidate and the date variable, reflecting the data's influence.
-Also, the posterior narrowing suggests that the model successfully extracted information from the data, reducing uncertainty around parameter estimates compared to the prior.
-model_data <- read_parquet(here::here("data/02-analysis_data/model_data.parquet"))
+In Figure~\ref{fig-ppcheckandposteriorvsprior-2} we compare the
+posterior with the prior. This shows the prior for each parameter is
+centered around zero, but the posterior shows more precise estimates for
+each candidate and the date variable, reflecting the data's influence.
+Also, the posterior narrowing suggests that the model successfully
+extracted information from the data, reducing uncertainty around
+parameter estimates compared to the prior. model\_data \textless-
+read\_parquet(here::here(``data/02-analysis\_data/model\_data.parquet''))
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-pp_check(model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
+\begin{figure}
 
-posterior_vs_prior(model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+\begin{minipage}[t]{0.50\linewidth}
 
-#| echo: false
-#| warning: false
-#| message: false
-posterior_predictions <- posterior_predict(model, draws = 100)
-ppc_dens_overlay(y = data_filtered$average_pct/100, yrep = posterior_predictions) +
-  labs(title = "Posterior Predictive Check",
-       x = "Rate of support",
-       y = "Density")
-```
+{\centering
 
-## Diagnostics
+\raisebox{-\height}{
 
-@fig-stanareyouokay-1 is a trace plot.
-It shows chain mixing, stationarity and no drifting.
-This suggests that the model's MCMC sampling achieved convergence for each parameter.
-The chains are well-mixed and stationary, providing confidence in the posterior estimates derived from this sampling process.
+\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-1.pdf}
 
-@fig-stanareyouokay-2 is a Rhat plot.
-It shows the Rhat values for the parameters estimated in the model.
-Values close to 1 indicate that the chains have mixed well and the posterior distribution has been adequately explored.
-This suggests that the model has converged successfully and the estimates are reliable for inference.
+}
 
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+}
 
-plot(model, "trace")
+\subcaption{\label{fig-ppcheckandposteriorvsprior-1}Posterior prediction
+check}
+\end{minipage}%
+%
+\begin{minipage}[t]{0.50\linewidth}
 
-plot(model, "rhat")
-```
+{\centering
+
+\raisebox{-\height}{
+
+\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-2.pdf}
+
+}
+
+}
+
+\subcaption{\label{fig-ppcheckandposteriorvsprior-2}Comparing the
+posterior with the prior}
+\end{minipage}%
+\newline
+\begin{minipage}[t]{0.50\linewidth}
+
+{\centering
+
+\raisebox{-\height}{
+
+\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-3.pdf}
+
+}
+
+}
+
+\subcaption{\label{fig-ppcheckandposteriorvsprior-3}Posterior prediction
+check}
+\end{minipage}%
+
+\caption{\label{fig-ppcheckandposteriorvsprior}Examining how the model
+fits, and is affected by, the data}
+
+\end{figure}
+
+\hypertarget{diagnostics}{%
+\subsection{Diagnostics}\label{diagnostics}}
+
+Figure~\ref{fig-stanareyouokay-1} is a trace plot. It shows chain
+mixing, stationarity and no drifting. This suggests that the model's
+MCMC sampling achieved convergence for each parameter. The chains are
+well-mixed and stationary, providing confidence in the posterior
+estimates derived from this sampling process.
+
+Figure~\ref{fig-stanareyouokay-2} is a Rhat plot. It shows the Rhat
+values for the parameters estimated in the model. Values close to 1
+indicate that the chains have mixed well and the posterior distribution
+has been adequately explored. This suggests that the model has converged
+successfully and the estimates are reliable for inference.
+
+\begin{figure}
+
+\begin{minipage}[t]{0.50\linewidth}
+
+{\centering
+
+\raisebox{-\height}{
+
+\includegraphics{paper_files/figure-pdf/fig-stanareyouokay-1.pdf}
+
+}
+
+}
+
+\subcaption{\label{fig-stanareyouokay-1}Trace plot}
+\end{minipage}%
+%
+\begin{minipage}[t]{0.50\linewidth}
+
+{\centering
+
+\raisebox{-\height}{
+
+\includegraphics{paper_files/figure-pdf/fig-stanareyouokay-2.pdf}
+
+}
+
+}
+
+\subcaption{\label{fig-stanareyouokay-2}Rhat plot}
+\end{minipage}%
+
+\caption{\label{fig-stanareyouokay}Checking the convergence of the MCMC
+algorithm}
+
+\end{figure}
 
@@
 
-# References
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Best2024}{}}%
+Best, Ryan, Aaron Bycoffe, et al. 2024. {``National: President: General
+Election: 2024 Polls.''} \emph{FiveThirtyEight}.
+\url{https://projects.fivethirtyeight.com/polls/president-general/2024/national/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-boyce_swing_states}{}}%
+Boyce, Lily, Lazaro Gamio, Eli Murray, and Alicia Parlapiano. 2024.
+{``Tracking the Swing States for Harris and Trump.''} 2024.
+\url{https://www.nytimes.com/interactive/2024/us/elections/presidential-election-swing-states.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bayesplot}{}}%
+Gabry, Jonah, and Tristan Mahr. 2024. {``Bayesplot: Plotting for
+Bayesian Models.''} \url{https://mc-stan.org/bayesplot/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rstanarm}{}}%
+Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2024.
+{``Rstanarm: {Bayesian} Applied Regression Modeling via {Stan}.''}
+\url{https://mc-stan.org/rstanarm/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kimball_polling}{}}%
+Kimball, Spencer, Camille Mumford, and Matt Taglia. 2024. {``How
+Pollsters Have Adapted to Changing Technology and Voters Who Don't
+Answer the Phone.''} 2024.
+\url{https://theconversation.com/how-pollsters-have-adapted-to-changing-technology-and-voters-who-dont-answer-the-phone-240283}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-here}{}}%
+Müller, Kirill. 2020. \emph{Here: A Simpler Way to Find Your Files}.
+\url{https://CRAN.R-project.org/package=here}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
+R Core Team. 2022. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-arrow}{}}%
+Richardson, Neal, Ian Cook, Nic Crane, Dewey Dunnington, Romain
+François, Jonathan Keane, Dragoș Moldovan-Grünfeld, Jeroen Ooms, Jacob
+Wujciak-Jens, and Apache Arrow. 2024. \emph{Arrow: Integration to
+'Apache' 'Arrow'}. \url{https://CRAN.R-project.org/package=arrow}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-psychology_survey_response}{}}%
+Roger Tourangeau, Lance J. Rips, and Kenneth Rasinski. 2000. {``The
+Psychology of Survey Response.''} In \emph{The Psychology of Survey
+Response}, 23--61. Cambridge University Press.
+\url{https://doi.org/10.1017/CBO9780511819322.003}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-nyt_poll}{}}%
+The New York Times. 2024. \emph{You Ask, We Answer: How the Times/Siena
+Poll Is Conducted}. The New York Times.
+\url{https://www.nytimes.com/article/times-siena-poll-methodology.html\#link-7be11f8b}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
+D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
+4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-readr}{}}%
+Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2023. \emph{Readr: Read
+Rectangular Text Data}. \url{https://CRAN.R-project.org/package=readr}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-scales}{}}%
+Wickham, Hadley, Thomas Lin Pedersen, and Dana Seidel. 2023.
+\emph{Scales: Scale Functions for Visualization}.
+\url{https://CRAN.R-project.org/package=scales}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
+Xie, Yihui. 2024. \emph{Knitr: A General-Purpose Package for Dynamic
+Report Generation in r}. \url{https://yihui.org/knitr/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Zahn2024}{}}%
+Zahn, Max. 2024. {``What's at Stake for Elon Musk in the Presidential
+Election?''} \emph{ABC News}, November.
+\url{https://abcnews.go.com/Business/stake-elon-musk-presidential-election/story?id=115143069}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
+Zhu, Hao. 2024. \emph{kableExtra: Construct Complex Table with 'Kable'
+and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
+
+\end{CSLReferences}
+
+\end{document}

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Added information about initial electoral map.

@@
 The model is specified as a Generalized Linear Model (GLM) with a binomial family and a logit link function, appropriate for modeling binary or proportion-based outcomes.
+The United State's electoral college system operates under a winner takes all votes mechanic where all the electoral votes are allocated to whichever candidate receives the larger share of votes within that state.
+Therefore, our model considers states outside the realm of swing states to have allocated a certain number of electoral votes to each candidate wherein Donald Trump has 219 seats and Kamala Harrris has  226.
+This initial distribution of electoral votes is provided by New York Times' tracking of swing states [@boyce_swing_states].
+Our model will produce projected shares in each state from which the electoral votes of swing states will be allocated to each  candidate to predict the winner of the presidential election.
 
@@
 The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
-Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters @nyt_poll.
+Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters [@nyt_poll].
 This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information.
-From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population @nyt_poll.
+From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population [@nyt_poll].
 
@@
 However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
-In fact, according to an article by Emerson College, telephone polling has become entirely obsolete @kimball_polling.
+In fact, according to an article by Emerson College, telephone polling has become entirely obsolete [@kimball_polling].
 Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling.
@@
 Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
-Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% @nyt_poll.
+Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% [@nyt_poll].
 
@@
 This approach helps to minimize sampling error by ensuring that all significant voter subgroups are included, thus increasing the reliability of the poll’s predictions.
-It is standard practice for them to sample 1,000 respondents for their polls.
+It is standard practice for them to sample 1,000 respondents for their polls [@nytpoll].
 Using stratified sampling to have this sample size closely resemble that of the entire target population cuts costs and provides efficient real-time data.
@@
 Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources.
-With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is @tellingstories.
+With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is [@tellingstories].
 As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.
@@
 Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented.
-The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups @nyt_poll.
+The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups [@nyt_poll].
 Clarity is also a central focus in their questionnaire development.
@@
 This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions.
-Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses @psychology_survey_response.
+Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses [@psychology_survey_response].
 
@@
 Pollsters such as  New York Times have their metric for determining which  states are 'battleground states'.
-As of 2024, our methodology should direct all our resources to acquiring voting data on the following states (New York Times).
+As of 2024, our methodology should direct all our resources to acquiring voting data on the states discussed in the swing states section.
 This assumption results in each presidential candidate starting off with a set number of electoral votes.
@@
 
-According to 2024 polling data conducted by New York Times, the swing states are determined to be the following @boyce_swing_states:
+According to 2024 polling data conducted by New York Times, the swing states are determined to be the following [@boyce_swing_states]:
 
@@
 Although online panels offer an imperfect solution to the limited resources our team will work with, there are remedies that can address underrepresentation brought by selection bias.
-As NYC and Siena College does, post-survey weighting can help us represent our target population more accurately.
+As with NYC and Siena College, post-survey weighting can help us represent our target population more accurately.
 This is an effective way to adjust our sample based on demographic data and historical turnout patterns within each state.
@@
 ###   Referral Mechanics
-To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey.
+To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey [@tellingstories].
 Each referral allows the original respondent to gain an additional entry in the lottery, increasing their chances of winning.
@@
 
-# Structure
+# Preamble
 
-## Preamble
+## Title: 2024 Presidential Election Poll Data
 
-Title: 2024 Presidential Election Poll Data
+## Introduction:
 
-Introduction: Thank you for your participation in our $5,000 giveaway program.
+Thank you for your participation in our $5,000 giveaway program.
 
@@
 
-Referral Code (please ignore if inapplicable)
+## Referral Code (please ignore if inapplicable)
 
-If you have entered a referral code above, please indicate the relationship with the referee from the best choice below.
+## If you have entered a referral code above, please indicate the relationship with the referee from the best choice below.
 	Friend
@@
 
-## Eligibility
-Do you meet your state's residency requirements?
+# Eligibility
+## Do you meet your state's residency requirements?
 	Yes
@@
 	Please select "N/A" from the options below if you reside in North Dakota. 
-Which of the following best describes you?
+## Which of the following best describes you?
 	I am registered to vote
@@
 	N/A
-Full Name (For identification of $5,000 cash winner)
-From which state will you be vote for the next president of the United States of America?
-Where can we reach you when we announce the winner?
+## Full Name (For identification of $5,000 cash winner)
+	Please type your response
+
+## From which state will you be casting your ballot for the presidential candidate?
+	Please select a state from the dropdown menu below
+## Where can we reach you when we announce the winner?
 	E-mail
@@
 	Other…
-Contact information
-**We will not use this for any other purpose than to announce winners. It will only be used to reach our lucky winner for instructions on receiving the cash prize.
-Which of the following age groups best describes you?
+## Contact information **We will not use this for any other purpose than to announce winners. It will only be used to reach our lucky winner for instructions on receiving the cash prize.**
+	Please type your response
+## Which of the following age groups best describes you?
 	18-25
@@
 	Under 18
-Which of the following best describes you?
+## Which of the following best describes you?
 	American Indian or Alaskan Native
@@
 	Other…
-What is your gender?
+## What is your gender?
 	Male
@@
 	Other…
-Which of the following situations best describe you?
+## Which of the following situations best describe you?
 	I did not vote in the 2020 presidential election
@@
 	I voted in the 2020 presidential election
-How likely are you to vote in the upcoming election?
-Very unlikely
+## How likely are you to vote in the upcoming election from a scale of 1 to 3? 1 is very unlikely and 3 is very likely.
+
 	1
@@
 	3
-Very likely
-Have you attended a presidential rally or their campaigns this year?
+## Have you attended a presidential rally or their campaigns this year?
 	Yes
@@
 	Only in the past
-On a scale of 1 to 3, how closely do you follow the presidential race?
-Not at all
+## On a scale of 1 to 3, how closely do you follow the presidential race? 1 is not at all and 5 is very closely.
 	1
@@
 	5
-Very closely
 
-## Party Affiliation
-Which party do you prefer a candidate to be chosen from?
+# Party Affiliation
+## Which party do you prefer a candidate to be chosen from?
 	Democratic Party's candidate
@@
 	Another Party's candidate
-In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
+## In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
 	Donald Trump
@@
 	Other…
-If planning to vote, which presidential candidate are you planning to vote for?
-If you are abstaining, please select which candidate you feel more strongly about.
+## If planning to vote, which presidential candidate are you planning to vote for? If you are abstaining, please select which candidate you feel more strongly about.
 	Donald Trump

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Included a pdf of survey in Appendix B instead of text.

@@
 
-https://docs.google.com/forms/d/117wC8f1rBW_bd5glEdiR-7823-02A3HiD5EzQuT1GVw/edit
+A copy of the PDF of our survey can be found in other/datasheet/Poll Survey - Google Forms.pdf
 
-# Preamble
-
-## Title: 2024 Presidential Election Poll Data
-
-## Introduction:
-
-Thank you for your participation in our $5,000 giveaway program.
-
-For entry, please complete the survey in its entirety below.
-Please be informed that your answers are strictly confidential and will, under no circumstances, be shared with any party, group, or persons of affiliation.
-
-$5,000 Cash Voucher Program Details: Completing the survey below qualifies as one entry into our giveaway.
-Each participant receives a unique entry identifier, and every entry will have an equal chance in our final random selection of the prize winner.
-Please note that each individual may complete only one survey.
-
-Referral Program: Our referral program offers you the chance to increase your odds of winning.
-After completing the survey, you’ll receive a unique referral code.
-If a friend or associate completes the survey using your code, your total number of entries doubles, effectively doubling your chances of winning the $5,000 prize.
-
-Finally, we wish to clarify that this survey is conducted purely for research purposes and is entirely unaffiliated with any political party, organization, or individual in a position of power.
-Our goal is to gain insight into the evolving political landscape and levels of public engagement.
-
-## Referral Code (please ignore if inapplicable)
-
-## If you have entered a referral code above, please indicate the relationship with the referee from the best choice below.
-	Friend
-	Associate
-	Relative
-	Other…
-
-# Eligibility
-## Do you meet your state's residency requirements?
-	Yes
-	No (End Survey)
-	Please select "N/A" from the options below if you reside in North Dakota. 
-## Which of the following best describes you?
-	I am registered to vote
-	I am not registered to vote
-	I plan to register
-	N/A
-## Full Name (For identification of $5,000 cash winner)
-	Please type your response
-
-## From which state will you be casting your ballot for the presidential candidate?
-	Please select a state from the dropdown menu below
-## Where can we reach you when we announce the winner?
-	E-mail
-	Telephone
-	Other…
-## Contact information **We will not use this for any other purpose than to announce winners. It will only be used to reach our lucky winner for instructions on receiving the cash prize.**
-	Please type your response
-## Which of the following age groups best describes you?
-	18-25
-	26-31
-	32-40
-	41-50
-	51-60
-	61-80
-	81-125
-	Under 18
-## Which of the following best describes you?
-	American Indian or Alaskan Native
-	Asian
-	African American
-	Hispanic or Latino
-	Native Hawaiian or Pacific Islander
-	White
-	Middle Eastern or North African
-	Other…
-## What is your gender?
-	Male
-	Female
-	Prefer not to say
-	Other…
-## Which of the following situations best describe you?
-	I did not vote in the 2020 presidential election
-	I planned to vote but wasn’t able to
-	I voted in the 2020 presidential election
-## How likely are you to vote in the upcoming election from a scale of 1 to 3? 1 is very unlikely and 3 is very likely.
-
-	1
-	2
-	3
-## Have you attended a presidential rally or their campaigns this year?
-	Yes
-	No
-	Only in the past
-## On a scale of 1 to 3, how closely do you follow the presidential race? 1 is not at all and 5 is very closely.
-	1
-	2
-	3
-	4
-	5
-
-# Party Affiliation
-## Which party do you prefer a candidate to be chosen from?
-	Democratic Party's candidate
-	Republican Party's candidate
-	Another Party's candidate
-## In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
-	Donald Trump
-	Joe Biden
-	Neither
-	Other…
-## If planning to vote, which presidential candidate are you planning to vote for? If you are abstaining, please select which candidate you feel more strongly about.
-	Donald Trump
-	Kamala Harris
-	Other...
+\includepdf[pages=-]{..other/datasheet/Poll Survey - Google Forms.pdf}
 

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Further explained data section and updated the abstract.

@@
 presidential election is shaping up to be a highly swing race, with polling data playing a crucial role in gauging public sentiment and forecasting the potential outcome.
-This paper aims to build a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election.
+This paper builds a predictive model using a poll-of-polls approach, aggregating data from multiple pollsters to forecast the winner of the upcoming election.
 The analysis incorporates polling data from various sources, filtered to include only high-quality pollsters with a numeric grade above 3, to ensure the reliability of the predictions.
+By incorporating the poll-of-polls approach with our model, we predict that Kamla Harris edges our Trump in the presidential election.
+Our model forecasts that with a 1%-4% margin lead in Pennsylvania, Wisconsin, Nevada, and Michigan, Kamala Harris will accumulate 276 electoral votes to win the election.
 Additionally, a detailed examination of one selected pollster’s methodology is conducted, highlighting strengths, weaknesses, and biases in the survey process.
@@
 presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race.
+Poll-of-polls approach allows us to access a wide breatdth of data that mitigates potential biases and errors committed by any single pollster.
 By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion.
@@
 The analysis will further explore the geographic distribution of support across key swing states, providing insights into the electoral landscape.
+Thus, our estimand will be the share of voter support for each presidential candidate in each swing state.
 Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts.

### 2024-11-04 paper/paper.qmd
Update paper.

--- 2024-11-04 paper/paper.qmd
@@
 The model is specified as a Generalized Linear Model (GLM) with a binomial family and a logit link function, appropriate for modeling binary or proportion-based outcomes.
-The United State's electoral college system operates under a winner takes all votes mechanic where all the electoral votes are allocated to whichever candidate receives the larger share of votes within that state.
-Therefore, our model considers states outside the realm of swing states to have allocated a certain number of electoral votes to each candidate wherein Donald Trump has 219 seats and Kamala Harrris has  226.
-This initial distribution of electoral votes is provided by New York Times' tracking of swing states [@boyce_swing_states].
-Our model will produce projected shares in each state from which the electoral votes of swing states will be allocated to each  candidate to predict the winner of the presidential election.
 
@@
 
-# Appendix A {-}
+# Appendix {-}
 
@@
 The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
-Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters [@nyt_poll].
+Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters @nyt_poll.
 This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information.
-From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population [@nyt_poll].
+From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population @nyt_poll.
 
@@
 However, reaching voters by phone has become more difficult due to low response rates requiring many attempts to secure responses from certain individuals (response rates are as  low as 2% at NYC).
-In fact, according to an article by Emerson College, telephone polling has become entirely obsolete [@kimball_polling].
+In fact, according to an article by Emerson College, telephone polling has become entirely obsolete @kimball_polling.
 Despite this, the phone methodology is still seen as effective for its ability to quickly reach a diverse voter pool across various states as well as seen as the golden standard for polling.
@@
 Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
-Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% [@nyt_poll].
+Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% @nyt_poll.
 
@@
 This approach helps to minimize sampling error by ensuring that all significant voter subgroups are included, thus increasing the reliability of the poll’s predictions.
-It is standard practice for them to sample 1,000 respondents for their polls [@nytpoll].
+It is standard practice for them to sample 1,000 respondents for their polls.
 Using stratified sampling to have this sample size closely resemble that of the entire target population cuts costs and provides efficient real-time data.
@@
 Although it is ideal to have probability based sampling increasingly resemble the demographic distribution quota with growing sample sizes, it is unfeasible to conduct such a large scale poll as this approach would encounter a limitation of resources.
-With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is [@tellingstories].
+With declining response rates and the difficulty of reaching voters, New York Times/Siena's nonprobability sampling is a more realistic and efficient method of polling than probability sampling is @tellingstories.
 As such, the stratified sampling approach allows New York Times/Siena to represent the entire target population with a sample size of 1,000.
@@
 Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented.
-The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups [@nyt_poll].
+The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups @nyt_poll.
 Clarity is also a central focus in their questionnaire development.
@@
 This is especially possible in phone interviews, where respondents may be more inclined to provide answers they perceive as socially acceptable rather than expressing their true opinions.
-Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses [@psychology_survey_response].
+Although the design aims to be fair, the influence of an interviewer’s presence may subtly affect responses @psychology_survey_response.
 
-\newpage
-
-# Appendix B {-}
+# Additional data details
 
@@
 Pollsters such as  New York Times have their metric for determining which  states are 'battleground states'.
-As of 2024, our methodology should direct all our resources to acquiring voting data on the states discussed in the swing states section.
+As of 2024, our methodology should direct all our resources to acquiring voting data on the following states (New York Times).
 This assumption results in each presidential candidate starting off with a set number of electoral votes.
@@
 
-According to 2024 polling data conducted by New York Times, the swing states are determined to be the following [@boyce_swing_states]:
+According to 2024 polling data conducted by New York Times, the swing states are determined to be the following @boyce_swing_states:
 
@@
 Although online panels offer an imperfect solution to the limited resources our team will work with, there are remedies that can address underrepresentation brought by selection bias.
-As with NYC and Siena College, post-survey weighting can help us represent our target population more accurately.
+As NYC and Siena College does, post-survey weighting can help us represent our target population more accurately.
 This is an effective way to adjust our sample based on demographic data and historical turnout patterns within each state.
@@
 ###  Referral Mechanics
-To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey [@tellingstories].
+To further broaden our reach without exponentially increasing advertising costs, we incorporate a referral system that rewards respondents for inviting others to complete the survey.
 Each referral allows the original respondent to gain an additional entry in the lottery, increasing their chances of winning.
@@
 
-A copy of the PDF of our survey can be found in other/datasheet/Poll Survey - Google Forms.pdf
+https://docs.google.com/forms/d/117wC8f1rBW_bd5glEdiR-7823-02A3HiD5EzQuT1GVw/edit
 
-\includepdf[pages=-]{..other/datasheet/Poll Survey - Google Forms.pdf}
+# Structure
 
-\newpage
+## Preamble
 
-# Additional data details
+Title: 2024 Presidential Election Poll Data
+
+Introduction: Thank you for your participation in our $5,000 giveaway program.
+
+For entry, please complete the survey in its entirety below.
+Please be informed that your answers are strictly confidential and will, under no circumstances, be shared with any party, group, or persons of affiliation.
+
+$5,000 Cash Voucher Program Details: Completing the survey below qualifies as one entry into our giveaway.
+Each participant receives a unique entry identifier, and every entry will have an equal chance in our final random selection of the prize winner.
+Please note that each individual may complete only one survey.
+
+Referral Program: Our referral program offers you the chance to increase your odds of winning.
+After completing the survey, you’ll receive a unique referral code.
+If a friend or associate completes the survey using your code, your total number of entries doubles, effectively doubling your chances of winning the $5,000 prize.
+
+Finally, we wish to clarify that this survey is conducted purely for research purposes and is entirely unaffiliated with any political party, organization, or individual in a position of power.
+Our goal is to gain insight into the evolving political landscape and levels of public engagement.
+
+Referral Code (please ignore if inapplicable)
+
+If you have entered a referral code above, please indicate the relationship with the referee from the best choice below.
+Friend
+Associate
+Relative
+Other…
+
+## Eligibility
+Do you meet your state's residency requirements?
+Yes
+No (End Survey)
+Please select "N/A" from the options below if you reside in North Dakota. 
+Which of the following best describes you?
+I am registered to vote
+I am not registered to vote
+I plan to register
+N/A
+Full Name (For identification of $5,000 cash winner)
+From which state will you be vote for the next president of the United States of America?
+Where can we reach you when we announce the winner?
+E-mail
+Telephone
+Other…
+Contact information
+**We will not use this for any other purpose than to announce winners. It will only be used to reach our lucky winner for instructions on receiving the cash prize.
+Which of the following age groups best describes you?
+18-25
+26-31
+32-40
+41-50
+51-60
+61-80
+81-125
+Under 18
+Which of the following best describes you?
+American Indian or Alaskan Native
+Asian
+African American
+Hispanic or Latino
+Native Hawaiian or Pacific Islander
+White
+Middle Eastern or North African
+Other…
+What is your gender?
+Male
+Female
+Prefer not to say
+Other…
+Which of the following situations best describe you?
+I did not vote in the 2020 presidential election
+I planned to vote but wasn’t able to
+I voted in the 2020 presidential election
+How likely are you to vote in the upcoming election?
+Very unlikely
+1
+2
+3
+Very likely
+Have you attended a presidential rally or their campaigns this year?
+Yes
+No
+Only in the past
+On a scale of 1 to 3, how closely do you follow the presidential race?
+Not at all
+1
+2
+3
+4
+5
+Very closely
+
+## Party Affiliation
+Which party do you prefer a candidate to be chosen from?
+Democratic Party's candidate
+Republican Party's candidate
+Another Party's candidate
+In the 2020 presidential election, who did you vote for?  If you did not vote, who would you have voted for?
+Donald Trump
+Joe Biden
+Neither
+Other…
+If planning to vote, which presidential candidate are you planning to vote for?
+If you are abstaining, please select which candidate you feel more strongly about.
+Donald Trump
+Kamala Harris
+Other...
 
@@
   theme_classic() +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  labs(title = "Posterior Predictive Check",
+       x = "Rate of support",
+       y = "Density")
 
@@
   coord_flip()
-
-#| echo: false
-#| warning: false
-#| message: false
-posterior_predictions <- posterior_predict(model, draws = 100)
-ppc_dens_overlay(y = data_filtered$average_pct/100, yrep = posterior_predictions) +
-  labs(title = "Posterior Predictive Check",
-       x = "Rate of support",
-       y = "Density")
 ```

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Better title and subtitle.

--- 2024-11-04 paper/paper.qmd
@@
 ---
-title: "Forecasting the 2024 U.S. Presidential Election"
-subtitle: "Using Aggregated Polling Data to Predict the Outcome of the 2024 Presidential Race"
+title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States"
+subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 3 of 4 Swing States"
 author: 

### 2024-11-04 paper/paper.qmd
Update paper.qmd
Final Paper Edit

@@
 The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
-Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters [@nyt_poll].
+Consequently, the target population is registered voters of the United States of America and the sampling frame is the voter file, a national list of registered voters from which NYC employs random sampling to create their pollsters [@nytpoll].
 This voter file contains information on more than 200 million Americans that includes information about their party affiliation, voting history, and  basic demographic information.
-From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population [@nyt_poll].
+From this sampling frame, respondents are randomly selected while balancing key demographic and political characteristics through both front-end sampling and post-survey weighting pursuant to appropriate representation of the entire target population [@nytpoll].
 
@@
 Non-response bias is a persistent challenge, and even though weighting helps, it's impossible to be certain that respondents are fully representative of those who do not respond.
-Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% [@nyt_poll].
+Experiments with alternative methods, such as mail surveys with incentives of cash vouchers have shown to increase response rate up to 30% [@nytpoll].
 
@@
 Each question is designed to ensure that respondents, regardless of their political views, feel that their perspectives are fairly represented.
-The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups [@nyt_poll].
+The team behind the poll spends substantial time crafting response options to reflect a balanced spectrum of views, minimizing potential response bias and enhancing the questionnaire's reliability across different demographic and ideological groups [@nytpoll].
 Clarity is also a central focus in their questionnaire development.
@@
 
-Although weighting adjustments helpsus represent our target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels since it will be advertised online.
+Although weighting adjustments helps us represent our target population more closely, there is nothing to stop respondents from outside our target population to participate in our panels since it will be advertised online.
 To produce accurate predictions of election results, our sample needs to be acquired from a target population that will participate in the election.
@@
 A copy of the PDF of our survey can be found in other/datasheet/Poll Survey - Google Forms.pdf
-
-\includepdf[pages=-]{..other/datasheet/Poll Survey - Google Forms.pdf}
-
-\newpage
-
-# Additional data details
 

### 2024-11-04 paper/paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 bibliography: references.bib
+header-includes:
+  - \usepackage{pdfpages}
 ---
@@
 
-\newpage
-
-# Appendix B {-}
+# Additional data details
 
@@
 This referral incentive taps into snowball sampling, where respondents refer people within their network to participate, expanding our pool of respondents organically.
+
 However, using snowball sampling in an election survey introduces potential biases, particularly the risk of overrepresentation of individuals with similar political views, as respondents are likely to refer to close contacts who may share similar ideologies.

### 2024-11-04 paper/paper.qmd
Update paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 ---
-title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Battleground States"
-subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 3 of 4 Swing States"
+title: "Forecast of the 2024 Presidential Election through the Lens of Turbulent Swing States"
+subtitle: "Kamala Harris Leads the Race With 276 Electoral Votes With Support in 4 of 7 Swing States"
 author: 
@@
 # Introduction
-The 2024 U.S.
-presidential election is shaping up to be one of the most closely watched and potentially pivotal elections in recent history.
-As public opinion shifts and political dynamics evolve, polling data has emerged as a critical tool for forecasting the outcome and understanding voter preferences.
-Polls provide a snapshot of where candidates stand at various points in time, reflecting the impact of campaigns, debates, and major events.
-However, the reliability and accuracy of individual polls can vary significantly based on methodology, sample size, and other factors, making it necessary to aggregate multiple sources of data for a more robust prediction.
+As the 2024 U.S.
+presidential election approaches, the race between Kamala Harris and Donald Trump reflects a deeply polarized electorate, particularly within key swing states.
+In an era where public opinion is continually shaped by a fast-paced media cycle and partisan divides, accurate election forecasting has never been more challenging or crucial.
+Swing states, where voter sentiment can tip the balance of the electoral college, have garnered particular attention.
+Traditional polls provide a snapshot of public opinion, but varying methodologies and sample biases limit their reliability.
+Thus, this paper seeks to bridge the gap in predictive accuracy by employing an aggregated “poll-of-polls” approach focused on capturing nuanced insights into voter behavior within these pivotal states.
 
-This paper aims to forecast the outcome of the 2024 U.S.
-presidential election by leveraging a "poll-of-polls" approach, which aggregates data from various pollsters to create a more comprehensive picture of the race.
-Poll-of-polls approach allows us to access a wide breatdth of data that mitigates potential biases and errors committed by any single pollster.
-By focusing on high-quality polls and conducting a detailed analysis of the polling trends for the two main candidates, Donald Trump and Kamala Harris, we seek to uncover patterns in voter support and potential factors influencing shifts in public opinion.
-Additionally, the paper examines the methodologies of different pollsters to assess their strengths and weaknesses, which can help identify possible biases in the aggregated data.
+This study builds a predictive model using aggregated polling data from a selection of high-quality pollsters, each rated above a minimum quality threshold.
+By concentrating on states historically known to sway election outcomes—such as Pennsylvania, Wisconsin, Nevada, and Michigan—this approach aims to provide a more resilient forecast against individual poll biases.
+The model examines demographic influences, candidate-specific factors, and recent endorsements, all while accounting for each state’s unique political landscape.
+Additionally, this paper critiques traditional polling methods, suggesting improvements in sampling and weighting techniques to achieve greater external validity.
+Given the substantial financial and temporal constraints inherent in polling, we propose an idealized methodology to enhance forecasting accuracy within a manageable budget of $100,000.
 
-The analysis will further explore the geographic distribution of support across key swing states, providing insights into the electoral landscape.
-Thus, our estimand will be the share of voter support for each presidential candidate in each swing state.
-Finally, the paper presents an idealized polling methodology with a $100,000 budget, designed to improve the accuracy and representativeness of election forecasts.
-By integrating multiple data sources and critically evaluating polling practices, this study aims to contribute to the ongoing discussion on the role of polling in democratic processes and election forecasting.
+The results of this analysis reveal a tentative lead for Kamala Harris, projecting 276 electoral votes in her favor, slightly above the 270 required to win.
+While she holds narrow but consistent margins in four critical swing states, her lead remains precarious in light of late-stage shifts in voter sentiment.
+These results emphasize the importance of demographic factors—such as Harris’s appeal among younger and immigrant voters—as well as the impact of recent high-profile endorsements for Trump, which could mobilize his base.
+The analysis suggests that the 2024 election will likely hinge on voter turnout in these contested states, highlighting the significance of demographic-targeted campaigns and last-minute electoral efforts in shaping the final outcome.
 

### 2024-11-04 paper/paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 
-# Model
+# Model {#sec-model}
 In this analysis, we utilize a logistic regression model to predict polling percentages for the 2024 U.S.
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 ## Turbulent Margins
@@
 
-# Appendix A {-}
+# Appendix {-}
 
-#  Sampling Methodology Employed by New York Times and Siena College:
+# Sampling Methodology Employed by New York Times and Siena College {#sec-Methodology}
 
@@
 
-# Sampling Approach: Stratified Sampling
+# Sampling Approach: Stratified Sampling {#sec-stratified-sampling}
 
@@
 
-\newpage
-
-# Appendix B {-}
+# Additional data details {#sec-additional_data_details}
 

### 2024-11-04 paper/paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 
-# Appendix A {-}
+# Appendix A{-}
 
-#  Sampling Methodology Employed by New York Times and Siena College:
+## Sampling Methodology Employed by New York Times and Siena College {#sec-Methodology}
 
@@
 
-## Target Population and Sampling Frame
+### Target Population and Sampling Frame
 The poll targets registered voters in the United States, with a particular focus on voters in swing states for presidential races.
@@
 
-## Recruitment Methods
+### Recruitment Methods
 The poll relies on random digit dialing to reach voters, predominantly via cell phones.
@@
 
-## Non-Response Remedies
+### Non-Response Remedies
 With a response rate of 2%, there is valid concern over non-response bias underrepresenting certain demographics.
@@
 
-# Sampling Approach: Stratified Sampling
+## Sampling Approach: Stratified Sampling {#sec-stratified-sampling}
 
-##  Methodology
+###  Methodology
 The Times/Siena Poll employs a stratified random sampling approach to ensure that the sample accurately represents the diversity within the target population of registered voters in the United States.
@@
 
-## Advantages
+### Advantages
 Stratified sampling offers the advantage of higher precision in representing the population's diversity, as each subgroup is proportionally represented.
@@
 
-## Stratified Sampling over Random Sampling
+### Stratified Sampling over Random Sampling
 
@@
 
-## Challenges and Trade-offs
+### Challenges and Trade-offs
 
@@
 
-## Evaluation of Questionnaire Design in the Times/Siena Poll
+### Evaluation of Questionnaire Design in the Times/Siena Poll
 
-### Strengths
+#### Strengths
 
@@
 
-### Limitations
+#### Limitations
 
@@
 
-\newpage
-
-# Appendix B {-}
+# Appendix B{-}
 
@@
 
-# Budget Allocation
+## Budget Allocation
   Advertisements for sampling recruitment: $70,000
@@
 
-#  Idealized Questionnaire and Survey
+## Idealized Questionnaire and Survey
 
@@
 
-# Model details {#sec-model-details}
+## Model details {#sec-model-details}
 
-## Posterior predictive check
+### Posterior predictive check
 
@@
   coord_flip()
-
-#| echo: false
-#| warning: false
-#| message: false
-posterior_predictions <- posterior_predict(model, draws = 100)
-ppc_dens_overlay(y = data_filtered$average_pct/100, yrep = posterior_predictions) +
-  labs(title = "Posterior Predictive Check",
-       x = "Rate of support",
-       y = "Density")
 ```
 
-## Diagnostics
+### Diagnostics
 

### 2024-11-04 scripts/04-test_analysis_data.R
Update tests.

@@ -12,7 +12,7 @@ library(testthat)
 library(arrow)
 
 # Load the cleaned data from the specified data folder
-cleaned_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
+cleaned_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
 
 #### Test data ####
 
@@ -21,11 +21,6 @@ test_that("dataset includes only selected swing states", {
   swing_states <- c("Pennsylvania", "Georgia", "North Carolina", 
                     "Michigan", "Arizona", "Wisconsin", "Nevada")
   expect_true(all(cleaned_data$state %in% swing_states))
-})
-
-# Test that the dataset contains no missing values
-test_that("dataset has no missing values", {
-  expect_true(all(!is.na(cleaned_data)))
 })
 
 # Test that the `population` column contains only "rv" entries

### 2024-11-04 scripts/00-simulate_data.R
Update simulation.

@@ -1,9 +1,9 @@
 #### Preamble ####
 # Purpose: Simulates a dataset of US electoral divisions, including the 
 #state and party that won each division.
-# Author: Rui Hu, 
+# Author: Rui Hu
 # Date: 22 October 2024
-# Contact: hr.hu@mail.utoronto.ca, 
+# Contact: hr.hu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
 

### 2024-11-04 scripts/02-download_data.R
Update download data.

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from the website Fivethirtyeight.
-# Author: Rui Hu, 
+# Author: Rui Hu
 # Date: 21 October 2024
-# Contact: hr.hu@mail.utoronto.ca, 
+# Contact: hr.hu@mail.utoronto.ca
 # License: N/A
 # Pre-requisites: N/A
 

### 2024-11-04 scripts/05-exploratory_data_analysis.R
Update exploratory data.

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models voter support for U.S. 2024 presidential candidates in key swing states,
+#          analyzing polling trends and predicting election outcomes.
+# Author: Andy Jiang
+# Date: 30 October 2024
+# Contact: ayx.jiang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: N\A
+# Any other information needed? N\A
 
 
 #### Workspace setup ####
@@ -13,19 +14,19 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
+data_filtered <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
 ### Model data ####
-first_model <-
+model <- 
   stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
+    formula = pct ~ end_date_numeric + candidate_name, 
+    data = data_filtered, 
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+    seed = 304
   )
+summary(model)
 
 
 #### Save model ####

### 2024-11-04 scripts/06-model_data.R
Update model data.

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models a Bayesian regression model to predict polling trends for the 2024 U.S. Presidential Election.
+# Author: Rui Hu
+# Date: 4 November 2024
+# Contact: hr.hu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: N\A
+# Any other information needed? N\A
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/07-replications.R
Update replication.

@@ -1,19 +1,19 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Replicates and visualizes key polling trends and support graphs for the 2024 U.S. Presidential Election.
+# Author: Rui Hu, Andy Jiang, Onon Burentuvshin
+# Date: 4 November 2024
+# Contact: hr.hu@mail.utoronto.ca, ayx.jiang@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: N\A
+# Any other information needed? N\A
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(arrow)
 
 #### Load data ####
-# [...ADD CODE HERE...]
+polling_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
 
 
 

### 2024-11-04 paper/paper.qmd
Update paper.

@@
 bibliography: references.bib
-header-includes:
-  - \usepackage{pdfpages}
 ---
@@
 The analysis suggests that the 2024 election will likely hinge on voter turnout in these contested states, highlighting the significance of demographic-targeted campaigns and last-minute electoral efforts in shaping the final outcome.
+
+In the **Data** section (see [Section 2](#sec-data)), we describe the sources and processing steps involved in preparing our dataset.
+Following that, the **Model** section (see [Section 3](#sec-model)) outlines the statistical model used to analyze the data and make predictions.
+
+The **Results** section (see [Section 4](#sec-result)) provides an overview of the model's forecasts and key findings, while the **Discussion** (see [Section 5](#sec-discussion)) interprets these results and considers broader implications.
+For additional technical information, including detailed model specifications, refer to the **Model Details** subsection (see [Section 5.1](#sec-model-details)).
 
@@
 
-# Results
+# Results {#sec-result}
 The analysis of polling data across key swing states for the 2024 U.S.
